---
title: "Resonance - Radiology multicolinearity"
output:
  html_document: default
  pdf_document: default
always_allow_html: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo=FALSE, include=FALSE}
library(data.table)
library(magrittr)
library(haven)
library(DiagrammeR)
library(glue)
library(kableExtra)
library(htmltools)
library(tidyverse)
library(ppcor)

source("utils.R")

dades <- read_sav('../data/BASEDATOSSRS.FINAL_152pacientes.sav') %>% as.data.frame()
setDT(dades)

noves_columnes <- c( "@_Global_Tilt", "@_LIVS1", "@_RLL", "@_RPV", "@_RSA")
for(var_name in noves_columnes){
  setnames(dades, var_name, gsub("@_", "", var_name, fixed=TRUE))
}
 
```

```{r echo=FALSE}
grViz('
digraph rmarkdown {

  graph [
    rankdir = UD
  ]
  
  node [
    shape=circle,
    fixedsize=true,
    width=1.2,
    style=filled,
    fontsize=15
    ]

 
  P[label="Age\nSex\nPrior-S\nCurveType\nSeguimiento"]
  U[label="Unobserved", style="dashed"]
  M[label="SF36_MCS"]
  S[label="Surgery"]
  R[label="Radiology (Post-T)"]
  O[label="Outcome"]
  RQ[label="Reintervention"]
  RS[label="Resonance"]
  
  
  P -> S
  P -> M
  M -> O
  P -> R
  U -> R
  S -> R
  R -> O[minlen=3]
  S -> M
  P -> O
  U -> S
  U -> M
  U -> O
  S -> RQ
  RQ -> R
  U -> RQ
  P -> RQ
  RQ -> M
  RQ -> RS
  S -> RS
  P -> RS
  U -> RS
  RS -> O
  
  {
    rank=same
    M
    R
    RS
  }
  
}                  
')
```

```{r}
outcomes <- c(
  "NRS_back__Back_pain__Average",
  "SF36_PCS",
  "EQ_5D_5L_SP",
  "ODI_2_FU_FORMULA",
  "SRS22__Self_image__Appearance",
  "SF36_MCS"
)

surgery <- c(
  "NIVELES_LIBRES_LUMBARES",
  "RECIRUGÃAS"
)

radiology <- c(
  "LIVS1",
  "Coronal_Balance_C7PL_to_CSVL",
  "RLL_ABS",
  "RPV_ABS",
  "RSA_ABS",
  "LDI_ABS"
)

resonance <- c(
  # "PFIRMANN_L3_L4_RECODE",
  "PFIRMANN_L4_L5_RECODE",
  "PFIRMANN_L5_SI_RECODE",
  "MODIC_L3_L4_RECODE",
  "MODIC_L4_L5_RECODE",
  "MODIC_L5_SI_RECODE"
)

confounders <- c(
  "EDAD_FU",
  "Gender",
  "Previous_surgery__LEV"
)
```

<!-- ```{r echo=FALSE} -->
<!-- get_type <- function(col_data){ -->
<!--   if( na.omit(col_data) %>% uniqueN == 2){ -->
<!--     return('classification') -->
<!--   }else{ -->
<!--     return('regression') -->
<!--   } -->
<!-- } -->
<!-- ``` -->

<!-- # Multicolinearity of radiology variables with respect  -->

<!-- ```{r} -->
<!-- vifs_list <- list() -->
<!-- for(var_ in radiology){ -->
<!--   dt <- dades[, .SD, .SDcols = c(resonance,confounders, surgery, var_)] -->

<!--   formula <- glue("{var_} ~ .") -->
<!--   type <- get_type(dt[, ..var_]) -->
<!--   if( type == "regression"){ -->
<!--     model <- lm(formula, data=dt %>% na.omit) -->
<!--   }else{ -->
<!--     model <- glm(formula, data=dt %>% na.omit,  -->
<!--                  family = 'binomial') -->
<!--   } -->

<!--   vifs <- car::vif(model) %>% as.data.frame -->
<!--   vifs['variable'] <- vifs %>% row.names -->
<!--   vifs <- data.table(vifs) -->
<!--   vifs_list[[var_]] <- vifs %>% .[, .SD, .SDcols = c('variable', 'GVIF')] %>%  -->
<!--     .[variable %chin% resonance] %>%  -->
<!--     .[, radiology := var_] -->
<!-- } -->
<!-- rbindlist(vifs_list) %>% dcast(variable~radiology, value.var = "GVIF") -->
<!-- ``` -->


<!-- ```{r} -->
<!-- vifs_list <- list() -->
<!-- for(var_ in resonance){ -->
<!--   dt <- dades[, .SD, .SDcols = c(radiology,confounders, surgery, var_)] -->

<!--   formula <- glue("{var_} ~ .") -->
<!--   type <- get_type(dt[, ..var_]) -->
<!--   if( type == "regression"){ -->
<!--     model <- lm(formula, data=dt %>% na.omit) -->
<!--   }else{ -->
<!--     model <- glm(formula, data=dt %>% na.omit,  -->
<!--                  family = 'binomial') -->
<!--   } -->

<!--   vifs <- car::vif(model) %>% as.data.frame -->
<!--   vifs['variable'] <- vifs %>% row.names -->
<!--   vifs <- data.table(vifs) -->
<!--   vifs_list[[var_]] <- vifs %>% .[, .SD, .SDcols = c('variable', 'GVIF')] %>%  -->
<!--     .[variable %chin% radiology] %>%  -->
<!--     .[, expl_var := var_] -->
<!-- } -->
<!-- rbindlist(vifs_list) %>% dcast(variable~expl_var, value.var = "GVIF") -->
<!-- ``` -->


## Partial correlations

Partial correlations: correlations between two variables, once the effect of confounders have been removed. 

For the case of resonance and radiology, confounders can be considered the list of confounders, but also surgical variables. 

We have used the function `pcor.test` from the `ppcor` R package. The following table shows partial correlations (with p.values testing whether these are zero or not in parenthesis)

```{r echo=FALSE, comment=""}
dt <- dades[, .SD, .SDcols = c(surgery, confounders, resonance, radiology)] %>% na.omit

prev <- model.matrix(Gender~`Previous_surgery__LEV`, dt)[, -1]
dt[, `Previous_surgery__LEV`:= NULL]
dt <- cbind(dt, prev)

results_res <- c()
results_rad <- c()
results <- c()
for(res_ in resonance){
  for(rad_ in radiology){
    part_cor <- pcor.test(
      dt[, get(res_)],
      dt[, get(rad_)],
      dt[, .SD, .SDcols=setdiff(dt %>% colnames, c(resonance, radiology))]
    )
    results_res <- c(results_res, res_)
    results_rad <- c(results_rad, rad_)
    results <- c(results, glue("{part_cor[1] %>% round(3)} ({part_cor[2] %>% round(3)})") )
  }
}
results <- data.table(resonance=results_res, radiology=results_rad, partial_corr = results)
results %>% dcast(resonance~radiology, value.var = 'partial_corr') %>% 
  kable %>% kable_styling()
```
## Correlations

<!-- ```{r, comment=""} -->
<!-- cors <- cor(dt[, .SD, .SDcols = c(resonance, radiology)]) %>% round(4) -->
<!-- ind_rows <- rownames(cors) %>% sapply(function(x) x %in% c(radiology)) -->
<!-- ind_cols <- colnames(cors) %>% sapply(function(x) x %in% c(resonance)) -->
<!-- cors[ind_rows, ind_cols] -->
<!-- ``` -->

```{r comment="", echo=FALSE}
results_res <- c()
results_rad <- c()
results <- c()
for(res_ in resonance){
  for(rad_ in radiology){
    cor_val <- cor(
      dt[, get(res_)],
      dt[, get(rad_)]
    )
    cor_p_val <- cor.test(
      dt[, get(res_)],
      dt[, get(rad_)]
    )$p.value
    results_res <- c(results_res, res_)
    results_rad <- c(results_rad, rad_)
    results <- c(results, glue("{cor_val %>% round(3)} ({cor_p_val %>% round(3)})") )
  }
}
results <- data.table(resonance=results_res, radiology=results_rad, correlation = results)
results %>% dcast(resonance~radiology, value.var = 'correlation') %>%
  kable %>% kable_styling()
```


