---
title: "Descriptive Stats"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_knit$set(
  echo = TRUE, 
  root.dir=normalizePath('../')
)
```

```{r echo=FALSE, warning=FALSE, include=FALSE}
library(readxl)
library(data.table)
library(magrittr)
library(yaml)
library(glue)
f <- glue


xls_path <- 'data/ESSG extraction July 2020_3.xlsx'

clinical_data <- read_excel(xls_path) %>% 
  as.data.table()

valid_patients <- clinical_data[
  `st1. Date of Stage 1` %>% as.Date() < as.Date('2018-07-31'), 
  `Code of the patient` %>% unique
]
clinical_data %<>% .[`Code of the patient` %in% valid_patients]

setnames(
  clinical_data, 
  'SRS22 -SI_First Visit', 
  'SRS22 - Self image / Appearance_First Visit'
)
setnames(
  clinical_data, 
  'SRS22 - MH_First Visit', 
  'SRS22 - Mental health_First Visit'
)
setnames(
  clinical_data, 
  'SRS22 - Function_First Visit', 
  'SRS22 - Function / Activity_First Visit'
)

clinical_data[, 
  `Pelvic Fixation` := grepl(
    'Iliac', 
    `Posterior Instrumented Fusion: Upper / Lower Levels`, 
    fixed=TRUE
  )] %>% 
  .[, `Pelvic Fixation` := ifelse(`Pelvic Fixation` == TRUE, 'Yes', 'No')]


vars <- read_yaml('code/descriptive.yml')

stats_fun <- function(variable){
  if( class(variable) == 'numeric' ){
    return( list(
      mean = mean(variable, na.rm=TRUE),
      sd = sd(variable, na.rm = TRUE)
    ))
  }else{
    res_table <- table(variable)
    return(list(
      table = res_table, 
      proportion = prop.table(res_table)
    ))
  }
}

total_patients <- clinical_data[, `Code of the patient` %>% uniqueN]

```


Number of Patients with 'st1. Date of Stage 1' < '2018-07-31':
`r total_patients`

### Demographics
```{r echo=FALSE, comment=""}
for(var_ in vars$demographics ){
  cat(var_)
  cat('\n')
  res <- stats_fun(clinical_data[[var_]])
  for( res_name in names(res) ){
    print(res_name)
    print(res[[res_name]])
  }
  cat('\n\n')
}
```


### Radiology
```{r echo=FALSE, comment=""}
for(var_ in vars$radiology ){
  var_2y <- "2Y. {var_}" %>% f
  var_5y <- "5Y. {var_}" %>% f
  vars_years <- c(var_, var_2y, var_5y)
  for(var_y in vars_years){
    cat(var_y)
    cat('\n')
    res <- stats_fun(clinical_data[[var_y]])
    for( res_name in names(res) ){
      print(res_name)
      print(res[[res_name]])
    }
    cat('\n\n')
  }
}
```


### Quality of Life
```{r echo=FALSE, comment=""}
for(var_0 in vars$quality ){
  var_ <- "{var_0}_First Visit" %>% f
  var_2y <- "2Y. {var_0}" %>% f
  var_5y <- "5Y. {var_0}" %>% f
  vars_years <- c(var_, var_2y, var_5y)
  for(var_y in vars_years){
    cat(var_y)
    cat('\n')
    res <- stats_fun(clinical_data[[var_y]])
    for( res_name in names(res) ){
      print(res_name)
      print(res[[res_name]])
    }
    cat('\n\n')
  }
}
```


### Surgery
```{r echo=FALSE, comment=""}
for(var_ in vars$surgery ){
  cat(var_)
  cat('\n')
  res <- stats_fun(clinical_data[[var_]])
  for( res_name in names(res) ){
    print(res_name)
    print(res[[res_name]])
  }
  cat('\n\n')
}
```
