---
title: "5y complications analysis"
output: html_document
---

  
```{r setup, include=FALSE}
knitr::opts_knit$set(
  echo = FALSE, 
  root.dir=normalizePath('../../'),
  warning=FALSE, 
  comment="",
  message=FALSE
)
```

```{r warning=FALSE, echo=FALSE, include=FALSE}
library(stringr)
library(ggplot2)
library(zeallot)
library(gridExtra)
library(DiagrammeR)

source('code/five_years/five_years-utils.R')

ncols_plots <- 2

outcomes <- c(
  '5Y. ODI - Score (%)', '5Y. SRS22 - SRS Subtotal score', '5Y. SF36 - PCS', '5Y. SF36 - MCS'
)

c(data_set_0, predictive_vars, .) %<-% get_data(clean=FALSE)
data_set <- data_set_0 %>% 
  .[Site != "MAD Op"] %>% 
  copy

valid_patients <- data_set[, `Code of the patient`] %>% unique

xls_path <- 'data/ESSG extraction December 2020 - DEF.xlsx'

complications <- read_excel(xls_path, sheet='Complications') %>%
  as.data.table %>%
  .[`Complication Impact` == 'Major Complication'] %>% 
  .[`Code of the patient` %in% valid_patients]


reinterventions <- read_excel(XLS_PATH, sheet = "Revision surgeries") %>%
  data.table %>% 
  .[`Code of the patient` %in% valid_patients]

data_set_0 %>% 
  .[, .(
    `Code of the patient`, 
    stage_date=`st1. Date of Stage 1`
  )]  %>% 
  rbind(
    reinterventions %>% 
      .[, .(
        `Code of the patient`, 
        stage_date=`st1. Date of Stage`
      )]    
  ) %>% 
  .[!is.na(stage_date)] %>% 
  .[, diff_years:=difftime(stage_date, min(stage_date), units = "days")/365, 
    `Code of the patient`] %>% 
  .[diff_years > 0] ->
  reinterventions


demographics <- read_yaml('code/five_years/demographic.yml')
demographics_all <- demographics %>% unlist


outcomes %>% 
  lapply(. %>% str_replace_all('5', '2')) ->
  outcomes_2y
names(outcomes_2y) <- outcomes

outcomes %>% 
  lapply(. %>% str_replace_all('5', '6')) ->
  outcomes_6y
names(outcomes_6y) <- outcomes

outcomes %>% 
  sapply(. %>% get_base_outcome(first_visit=TRUE)) ->
  base_outcomes 

for( outcome in names(outcomes_6y)){
  outcome_6y <- outcomes_6y[[outcome]]
  data_set %<>%
    .[is.na(get(outcome)), c(outcome_6y) := get(outcome)]
}

outcome_2y <- outcomes_2y[[1]]
outcome <- outcomes[[1]]


study_vars <- c(
  outcomes, outcomes_2y %>% unlist, demographics_all, base_outcomes, 'Code of the patient'
) %>% unique
data_set %<>% 
  .[Study=='Op'] %>% 
  .[, .SD, .SDcols=study_vars] %>% 
  .[, followup_2y := 'has_followup'] %>% 
  .[is.na(get(outcome_2y)), followup_2y := 'no_followup'] %>% 
  .[, followup_5y := 'has_followup'] %>% 
  .[is.na(get(outcome)), followup_5y := 'no_followup'] 


```

#### Only Major Complications

```{r echo=FALSE}
grViz('
digraph rmarkdown {

  graph [
    rankdir = UD
  ]
  
  node [
    shape=circle,
    fixedsize=true,
    width=1.2,
    style=filled,
    fillcolor=aquamarine2,
    fontsize=15
    ]

 
  D[label="Demographic"]
  P[label="Personality", style="dashed"]
  R[label="Radiologic\n(Deformity)"]
  O[label="Outcome"]
  H[label="Quality of\nLife"]
  T[label="Treatment"]
  C[label="Complications"]
  
  D -> R 
  D -> O
  R -> O
  P -> R
  P -> H
  D -> H
  H -> O
  H -> T
  T -> O
  R -> T
  T -> C
  H -> C
  D -> C
  C -> O
  R -> C
  
  
  {rank=same; P;D}
  {rank=same; R;H}
  {rank=same; T}
  {rank=same; C}
  {rank=same; O}
}                  
')
```


```{r echo=FALSE}
complication_types <- complications[, `Category of the complication` %>% unique]
complication_types <- complication_types %!in% "Central neurologic complications"


patients_complications_5y <- complications %>%
  .[`Days since surgery` >= 365*2 ] %>% 
  .[`Days since surgery` < 365*5 ] %>% 
  .[`Category of the complication` %in% complication_types, `Code of the patient`]
patients_complications_2y <- complications %>%
  .[`Days since surgery` < 365*2 ] %>% 
  .[`Category of the complication` %in% complication_types, `Code of the patient`]

data_ <- data_set %>%
  copy %>%
  .[, complication_before_2y:='No'] %>%
  .[`Code of the patient` %in% patients_complications_2y, complication_before_2y:='Yes'] %>% 
  .[, complication_2y_5y:='No'] %>%
  .[`Code of the patient` %in% patients_complications_5y, complication_2y_5y:='Yes']

```

## Stats

```{r echo=FALSE, comment=""}
data_[, .(has_followup_2y=mean(followup_2y=='has_followup') %>% round(3)),  complication_before_2y]
```

```{r echo=FALSE, comment=""}
data_[, .(has_followup_5y=mean(followup_5y=='has_followup') %>% round(3)),  complication_before_2y]
```

<!-- ```{r echo=FALSE} -->
<!-- data_[, .(has_followup_5y=mean(followup_5y=='has_followup') %>% round(3)),  complication_2y_5y] -->
<!-- ``` -->


```{r echo=FALSE}
complications_all <- read_excel(xls_path, sheet='Complications') %>%
  as.data.table %>% 
  .[`Code of the patient` %in% valid_patients]
```


### Major Complications before 2y
```{r echo=FALSE, comment=""}
complications_all %>%
  .[`Complication Impact` == 'Major Complication'] %>% 
  .[`Days since surgery` < 365*2 ] %>% 
  .[, table(`Category of the complication`)] %T>% 
  print %>% 
  prop.table()
```

### Major Complications between 2y and 5y
```{r echo=FALSE, comment=""}
complications_all %>%
  .[`Complication Impact` == 'Major Complication'] %>% 
  .[`Days since surgery` >= 365*2 ] %>% 
  .[`Days since surgery` < 365*5 ] %>% 
  .[, table(`Category of the complication`)] %T>% 
  print %>% 
  prop.table()
```

### Minor Complications before 2y
```{r echo=FALSE, comment=""}
complications_all %>%
  .[`Complication Impact` == 'Minor Complication'] %>% 
  .[`Days since surgery` < 365*2 ] %>% 
  .[, table(`Category of the complication`)] %T>% 
  print %>% 
  prop.table()
```

### Minor Complications between 2y and 5y
```{r echo=FALSE, comment=""}
complications_all %>%
  .[`Complication Impact` == 'Minor Complication'] %>% 
  .[`Days since surgery` >= 365*2 ] %>% 
  .[`Days since surgery` < 365*5 ] %>% 
  .[, table(`Category of the complication`)] %T>% 
  print %>% 
  prop.table()
```



### Reinterventions before 2 years
```{r echo=FALSE}
patients_all <- data_set[, `Code of the patient` %>% unique]

reinterventions %>% 
  .[diff_years < 2] ->
  reints_2y

patients_2y <- reints_2y[, `Code of the patient` %>% unique]

reinterventions %>% 
  .[2 <= diff_years] %>% 
  .[diff_years < 5] ->
  reints_2y_5y

patients_2y_5y <- reints_2y_5y[, `Code of the patient` %>% unique]

```

- Reinterventions before 2 years: `r reints_2y[, .N]`
- Proportion of patients with reintervention before 2 years: `r len(patients_2y) / len(patients_all)`

- Reinterventions between 2y and 5y: `r reints_2y_5y[, .N]`
- Proportion of patients with reintervention between 2y and 5y: `r len(patients_2y_5y) / len(patients_all)`


### Do complications before 2y affect 2y followup?

```{r echo=FALSE, comment=""}

conf_vars_ <- c(
  demographics$demographic,
  demographics$radiologic,
  base_outcomes
)

vars_ <- c(
  conf_vars_,
  "complication_before_2y",
  "followup_2y"
)

data_ %>% 
  .[, .SD, .SDcols=vars_] %>% 
  na.omit %>% 
  .[, followup_2y := ifelse(followup_2y=='has_followup', 1, 0)]  %>% 
  lm(followup_2y~., data=.) %>% summary %>% coefficients %>%  .[, c(1, 4)] %>% round(3)
```

### Do complications before 2y affect 5y followup?

```{r echo=FALSE, comment=""}

conf_vars_ <- c(
  demographics$demographic,
  demographics$radiologic,
  base_outcomes
)

vars_ <- c(
  conf_vars_,
  "complication_before_2y",
  "followup_5y"
)

data_ %>% 
  .[, .SD, .SDcols=vars_] %>% 
  na.omit %>% 
  .[, followup_5y := ifelse(followup_5y=='has_followup', 1, 0)]  %>% 
  lm(followup_5y~., data=.) %>% summary %>% coefficients %>%  .[, c(1, 4)] %>% round(3)
```


<!-- ### Do complications between 2y and 5y affect 2y followup? -->

<!-- ```{r echo=FALSE, comment=""} -->

<!-- conf_vars_ <- c( -->
<!--   demographics$demographic, -->
<!--   demographics$radiologic, -->
<!--   base_outcomes -->
<!-- ) -->

<!-- vars_ <- c( -->
<!--   conf_vars_, -->
<!--   "complication_2y_5y", -->
<!--   "followup_5y" -->
<!-- ) -->

<!-- data_ %>%  -->
<!--   .[, .SD, .SDcols=vars_] %>%  -->
<!--   na.omit %>%  -->
<!--   .[, followup_5y := ifelse(followup_5y=='has_followup', 1, 0)]  %>%  -->
<!--   lm(followup_5y~., data=.) %>% summary %>% coefficients %>% .[, c(1, 4)] %>% round(3) -->
<!-- ``` -->



