---
title: "5y complications analysis"
output:
  pdf_document: default
  html_document: default
always_allow_html: yes
---

```{r setup, include=FALSE}
knitr::opts_knit$set(
  echo = FALSE, 
  root.dir=normalizePath('../'),
  warning=FALSE, 
  comment="",
  message=FALSE
)
```

```{r warning=FALSE, echo=FALSE, include=FALSE}
library(stringr)
library(ggplot2)
library(zeallot)
library(gridExtra)
library(DiagrammeR)

source('five_years/five_years-utils.R')
```

# All

```{r echo=TRUE}
xls_path <- '../../data/Dataset 4th report 5Y - ONLY DPS.xlsx'
```

```{r warning=FALSE, echo=FALSE, include=FALSE}
c(data_set_0, predictive_vars, .) %<-% get_data(xls_path, clean=FALSE)
data_set <- data_set_0 %>% copy

data_set %<>% 
  .[, followup_2y := 
      !is.na(`2 YEAR VISIT - Date of visit`) | 
      !is.na(`3 YEAR VISIT - Date of visit`)] %>% 
  .[, followup_5y := 
      !is.na(`5 YEAR VISIT - Date of visit`) | 
      !is.na(`6 YEAR VISIT - Date of visit`)]
```

### Filters

```{r echo=FALSE}
# data_set %<>%
#   .[followup_2y==TRUE] %>%
#   .[`st1. Date of Stage` %>% as.Date() < as.Date('2016-6-1')]
```

```{r, echo=FALSE}
patients_all <- data_set[, `Code of the patient` %>% unique]
```

```{r, echo=FALSE}
complications_all <- read_excel(xls_path, sheet='Complications') %>%
  as.data.table %>% 
  .[`Code of the patient` %in% patients_all] 

complications_all[, Category := strsplit(
    `Category of the complication`, ":")[[1]][1],
    1:nrow(complications_all)]
```


```{r include=FALSE}
patient_2yFU <- data_set[followup_2y==TRUE, `Code of the patient` %>% unique]
patient_2y_5yFU <- data_set[followup_2y==TRUE & followup_5y==TRUE, `Code of the patient` %>% unique]
```



### Major Complications

```{r, echo=FALSE}
comp_type <- "Major Complication"
complications_all %>%
  .[`Code of the patient` %in% patient_2yFU] %>%
  .[`Complication Impact` == comp_type] %>% 
  .[`Days since surgery` < 365*2 ] ->
  comps_2y

# complications_all %>%
#   .[`Code of the patient` %in% patient_2yFU] %>%
#   .[`Days since surgery` < 365*2 ] %>%
#   .[, `Code of the patient` %>% uniqueN]->
#   elegible_2y
elegible_2y <- len(patient_2yFU)

patients_2y <- comps_2y[, `Code of the patient` %>% unique]

complications_all %>%
  .[`Code of the patient` %in% patient_2y_5yFU] %>% 
  .[`Complication Impact` == comp_type] %>% 
  .[`Days since surgery` >= 365*2 ] %>% 
  .[`Days since surgery` < 365*5 ] ->
  comps_2y_5y

complications_all %>%
  .[`Code of the patient` %in% patient_2y_5yFU] %>% 
  .[`Days since surgery` >= 365*2 ] %>% 
  .[`Days since surgery` < 365*5 ]  %>% 
  .[, `Code of the patient` %>% uniqueN] ->
  elegible_2y_5y

patients_2y_5y <- comps_2y_5y[, `Code of the patient` %>% unique]

patients_n <- len(patients_all)
patients_2y_n <- len(patients_2y)
patients_2y_5y_n <- len(patients_2y_5y)
p_val <- prop.test(c(patients_2y_n, patients_2y_5y_n), c(elegible_2y, elegible_2y_5y))$p.value
```

- Total patients: `r patients_n`

- Complications before 2 years: `r comps_2y[, .N]`
- Elegible patients with 2Y: `r elegible_2y`
- Patients with complications before 2 years: `r patients_2y_n`
- Proportion of patients with complications before 2 years: `r patients_2y_n / elegible_2y`

- Complications between 2y and 5y: `r comps_2y_5y[, .N]`
- Elegible patients with 2Y and 5Y: `r elegible_2y_5y`
- Patients with complications before 5 years: `r patients_2y_5y_n`
- Proportion of patients with complications between 2y and 5y: `r patients_2y_5y_n / elegible_2y_5y`

- p-value testing equality between proportions of complications: `r p_val`

```{r include=FALSE}
patients_2y_n_dp_major <- patients_2y_n
elegible_2y_dp_major <- elegible_2y
patients_2y_5y_n_dp_major <- patients_2y_5y_n
elegible_2y_5y_dp_major <- elegible_2y_5y
```

Complications 2Y

```{r comment="", echo=FALSE}
major_all <- complications_all %>%
  .[`Complication Impact` == comp_type] %>% 
  .[`Code of the patient` %in% patient_2yFU] %>% 
  .[`Days since surgery` < 365*2 ] %>% 
  .[, .(pats_n = uniqueN(`Code of the patient`)), Category]

major_all[, prop := pats_n/sum(major_all[, pats_n])]
major_all
```

Complications between 2Y and 5Y

```{r comment="", echo=FALSE}
major_all_25 <- complications_all %>%
  .[`Complication Impact` == comp_type] %>% 
  .[`Code of the patient` %in% patient_2y_5yFU] %>% 
  .[`Days since surgery` >= 365*2 ] %>% 
  .[`Days since surgery` < 365*5 ]  %>% 
  .[, .(pats_n = uniqueN(`Code of the patient`)), Category]

major_all_25[, prop := pats_n/sum(major_all_25[, pats_n])]
major_all_25
```


### Minor Complications

```{r, echo=FALSE}
comp_type <- "Minor Complication"
complications_all %>%
  .[`Code of the patient` %in% patient_2yFU] %>% 
  .[`Complication Impact` == comp_type] %>% 
  .[`Days since surgery` < 365*2 ] ->
  comps_2y

# complications_all %>%
#   .[`Code of the patient` %in% patient_2yFU] %>%
#   .[`Days since surgery` < 365*2 ] %>%
#   .[, `Code of the patient` %>% uniqueN]->
#   elegible_2y
elegible_2y <- len(patient_2yFU)

patients_2y <- comps_2y[, `Code of the patient` %>% unique]

complications_all %>%
  .[`Code of the patient` %in% patient_2y_5yFU] %>% 
  .[`Complication Impact` == comp_type] %>% 
  .[`Days since surgery` >= 365*2 ] %>% 
  .[`Days since surgery` < 365*5 ] ->
  comps_2y_5y

complications_all %>%
  .[`Code of the patient` %in% patient_2y_5yFU] %>% 
  .[`Days since surgery` >= 365*2 ] %>% 
  .[`Days since surgery` < 365*5 ]  %>% 
  .[, `Code of the patient` %>% uniqueN] ->
  elegible_2y_5y

patients_2y_5y <- comps_2y_5y[, `Code of the patient` %>% unique]

patients_n <- len(patients_all)
patients_2y_n <- len(patients_2y)
patients_2y_5y_n <- len(patients_2y_5y)
p_val <- prop.test(c(patients_2y_n, patients_2y_5y_n), c(elegible_2y, elegible_2y_5y))$p.value
```

- Total patients: `r patients_n`

- Complications before 2 years: `r comps_2y[, .N]`
- Elegible patients with 2Y: `r elegible_2y`
- Patients with complications before 2 years: `r patients_2y_n`
- Proportion of patients with complications before 2 years: `r patients_2y_n / elegible_2y`

- Complications between 2y and 5y: `r comps_2y_5y[, .N]`
- Elegible patients with 2Y and 5Y: `r elegible_2y_5y`
- Patients with complications before 5 years: `r patients_2y_5y_n`
- Proportion of patients with complications between 2y and 5y: `r patients_2y_5y_n / elegible_2y_5y`

- p-value testing equality between proportions of complications: `r p_val`

```{r include=FALSE}
patients_2y_n_dp_minor <- patients_2y_n
elegible_2y_dp_minor <- elegible_2y
patients_2y_5y_n_dp_minor <- patients_2y_5y_n
elegible_2y_5y_dp_minor <- elegible_2y_5y
```



Complications 2Y

```{r comment="", echo=FALSE}
minor_all <- complications_all %>%
  .[`Complication Impact` == comp_type] %>% 
  .[`Code of the patient` %in% patient_2yFU] %>% 
  .[`Days since surgery` < 365*2 ] %>% 
  .[, .(pats_n = uniqueN(`Code of the patient`)), Category]

minor_all[, prop := pats_n/sum(minor_all[, pats_n])]
minor_all
```

Complications between 2Y and 5Y

```{r comment="", echo=FALSE}
minor_all_25 <- complications_all %>%
  .[`Complication Impact` == comp_type] %>% 
  .[`Code of the patient` %in% patient_2y_5yFU] %>% 
  .[`Days since surgery` >= 365*2 ] %>% 
  .[`Days since surgery` < 365*5 ]  %>% 
  .[, .(pats_n = uniqueN(`Code of the patient`)), Category]

minor_all_25[, prop := pats_n/sum(minor_all_25[, pats_n])]
minor_all_25
```

# Non depuy

```{r echo=TRUE}
xls_path <- '../../data/ESSG Extraction_DEC_OP_ NON DePuy v7.xlsx'
```

```{r warning=FALSE, echo=FALSE, include=FALSE}
c(data_set_0, predictive_vars, .) %<-% get_data(xls_path, clean=FALSE)
data_set <- data_set_0 %>% copy

data_set %<>% 
  .[, followup_2y := 
      !is.na(`2 YEAR VISIT - Date of visit`) | 
      !is.na(`3 YEAR VISIT - Date of visit`)] %>% 
  .[, followup_5y := 
      !is.na(`5 YEAR VISIT - Date of visit`) | 
      !is.na(`6 YEAR VISIT - Date of visit`)]
```

### Filters

```{r echo=FALSE}
# data_set %<>%
#   .[followup_2y==TRUE] %>%
#   .[`st1. Date of Stage` %>% as.Date() < as.Date('2016-6-1')]
```

```{r, echo=FALSE}
patients_all <- data_set[, `Code of the patient` %>% unique]
```

```{r, echo=FALSE}
complications_all <- read_excel(xls_path, sheet='Complications') %>%
  as.data.table %>% 
  .[`Code of the patient` %in% patients_all] 

complications_all[, Category := strsplit(
    `Category of the complication`, ":")[[1]][1],
    1:nrow(complications_all)]
```


```{r include=FALSE}
patient_2yFU <- data_set[followup_2y==TRUE, `Code of the patient` %>% unique]
patient_2y_5yFU <- data_set[followup_2y==TRUE & followup_5y==TRUE, `Code of the patient` %>% unique]
```

### Major Complications

```{r, echo=FALSE}
comp_type <- "Major Complication"
complications_all %>%
  .[`Code of the patient` %in% patient_2yFU] %>% 
  .[`Complication Impact` == comp_type] %>% 
  .[`Days since surgery` < 365*2 ] ->
  comps_2y

# complications_all %>%
#   .[`Code of the patient` %in% patient_2yFU] %>%
#   .[`Days since surgery` < 365*2 ] %>%
#   .[, `Code of the patient` %>% uniqueN]->
#   elegible_2y
elegible_2y <- len(patient_2yFU)

patients_2y <- comps_2y[, `Code of the patient` %>% unique]

complications_all %>%
  .[`Code of the patient` %in% patient_2y_5yFU] %>% 
  .[`Complication Impact` == comp_type] %>% 
  .[`Days since surgery` >= 365*2 ] %>% 
  .[`Days since surgery` < 365*5 ] ->
  comps_2y_5y

complications_all %>%
  .[`Code of the patient` %in% patient_2y_5yFU] %>% 
  .[`Days since surgery` >= 365*2 ] %>% 
  .[`Days since surgery` < 365*5 ]  %>% 
  .[, `Code of the patient` %>% uniqueN] ->
  elegible_2y_5y

patients_2y_5y <- comps_2y_5y[, `Code of the patient` %>% unique]

patients_n <- len(patients_all)
patients_2y_n <- len(patients_2y)
patients_2y_5y_n <- len(patients_2y_5y)
p_val <- prop.test(c(patients_2y_n, patients_2y_5y_n), c(elegible_2y, elegible_2y_5y))$p.value
```

- Total patients: `r patients_n`

- Complications before 2 years: `r comps_2y[, .N]`
- Elegible patients with 2Y: `r elegible_2y`
- Patients with complications before 2 years: `r patients_2y_n`
- Proportion of patients with complications before 2 years: `r patients_2y_n / elegible_2y`

- Complications between 2y and 5y: `r comps_2y_5y[, .N]`
- Elegible patients with 2Y and 5Y: `r elegible_2y_5y`
- Patients with complications before 5 years: `r patients_2y_5y_n`
- Proportion of patients with complications between 2y and 5y: `r patients_2y_5y_n / elegible_2y_5y`

- p-value testing equality between proportions of complications: `r p_val`

```{r include=FALSE}
patients_2y_n_nondp_major <- patients_2y_n
elegible_2y_nondp_major <- elegible_2y
patients_2y_5y_n_nondp_major <- patients_2y_5y_n
elegible_2y_5y_nondp_major <- elegible_2y_5y
```



Complications 2Y

```{r comment="", echo=FALSE}
major_nondp <- complications_all %>%
  .[`Complication Impact` == comp_type] %>% 
  .[`Code of the patient` %in% patient_2yFU] %>% 
  .[`Days since surgery` < 365*2 ] %>% 
  .[, .(pats_n = uniqueN(`Code of the patient`)), Category]

major_nondp[, prop := pats_n/sum(major_nondp[, pats_n])]
major_nondp
```

Complications between 2Y and 5Y

```{r comment="", echo=FALSE}
major_nondp_25 <- complications_all %>%
  .[`Complication Impact` == comp_type] %>% 
  .[`Code of the patient` %in% patient_2y_5yFU] %>% 
  .[`Days since surgery` >= 365*2 ] %>% 
  .[`Days since surgery` < 365*5 ]  %>% 
  .[, .(pats_n = uniqueN(`Code of the patient`)), Category]

major_nondp_25[, prop := pats_n/sum(major_nondp_25[, pats_n])]
major_nondp_25
```

### Minor Complications

```{r, echo=FALSE}
comp_type <- "Minor Complication"
complications_all %>%
  .[`Code of the patient` %in% patient_2yFU] %>% 
  .[`Complication Impact` == comp_type] %>% 
  .[`Days since surgery` < 365*2 ] ->
  comps_2y

# complications_all %>%
#   .[`Code of the patient` %in% patient_2yFU] %>%
#   .[`Days since surgery` < 365*2 ] %>%
#   .[, `Code of the patient` %>% uniqueN]->
#   elegible_2y
elegible_2y <- len(patient_2yFU)

patients_2y <- comps_2y[, `Code of the patient` %>% unique]

complications_all %>%
  .[`Code of the patient` %in% patient_2y_5yFU] %>% 
  .[`Complication Impact` == comp_type] %>% 
  .[`Days since surgery` >= 365*2 ] %>% 
  .[`Days since surgery` < 365*5 ] ->
  comps_2y_5y

complications_all %>%
  .[`Code of the patient` %in% patient_2y_5yFU] %>% 
  .[`Days since surgery` >= 365*2 ] %>% 
  .[`Days since surgery` < 365*5 ]  %>% 
  .[, `Code of the patient` %>% uniqueN] ->
  elegible_2y_5y

patients_2y_5y <- comps_2y_5y[, `Code of the patient` %>% unique]

patients_n <- len(patients_all)
patients_2y_n <- len(patients_2y)
patients_2y_5y_n <- len(patients_2y_5y)
p_val <- prop.test(c(patients_2y_n, patients_2y_5y_n), c(elegible_2y, elegible_2y_5y))$p.value
```

- Total patients: `r patients_n`

- Complications before 2 years: `r comps_2y[, .N]`
- Elegible patients with 2Y: `r elegible_2y`
- Patients with complications before 2 years: `r patients_2y_n`
- Proportion of patients with complications before 2 years: `r patients_2y_n / elegible_2y`

- Complications between 2y and 5y: `r comps_2y_5y[, .N]`
- Elegible patients with 2Y and 5Y: `r elegible_2y_5y`
- Patients with complications before 5 years: `r patients_2y_5y_n`
- Proportion of patients with complications between 2y and 5y: `r patients_2y_5y_n / elegible_2y_5y`

- p-value testing equality between proportions of complications: `r p_val`

```{r include=FALSE}
patients_2y_n_nondp_minor <- patients_2y_n
elegible_2y_nondp_minor <- elegible_2y
patients_2y_5y_n_nondp_minor <- patients_2y_5y_n
elegible_2y_5y_nondp_minor <- elegible_2y_5y
```



Complications 2Y

```{r comment="", echo=FALSE}
minor_nondp <- complications_all %>%
  .[`Complication Impact` == comp_type] %>% 
  .[`Code of the patient` %in% patient_2yFU] %>% 
  .[`Days since surgery` < 365*2 ] %>% 
  .[, .(pats_n = uniqueN(`Code of the patient`)), Category]

minor_nondp[, prop := pats_n/sum(minor_nondp[, pats_n])]
minor_nondp
```

Complications between 2Y and 5Y

```{r comment="", echo=FALSE}
minor_nondp_25 <- complications_all %>%
  .[`Complication Impact` == comp_type] %>% 
  .[`Code of the patient` %in% patient_2y_5yFU] %>% 
  .[`Days since surgery` >= 365*2 ] %>% 
  .[`Days since surgery` < 365*5 ]  %>% 
  .[, .(pats_n = uniqueN(`Code of the patient`)), Category]

minor_nondp_25[, prop := pats_n/sum(minor_nondp_25[, pats_n])]
minor_nondp_25
```



<!-- # 2YFU -->

<!-- ```{r echo=TRUE} -->
<!-- xls_path <- '../../data/Dataset 4th report 5Y - ONLY DPS.xlsx' -->
<!-- ``` -->

<!-- ```{r warning=FALSE, echo=FALSE, include=FALSE} -->
<!-- c(data_set_0, predictive_vars, .) %<-% get_data(xls_path, clean=FALSE) -->
<!-- data_set <- data_set_0 %>% copy -->

<!-- data_set %<>%  -->
<!--   .[, followup_2y :=  -->
<!--       !is.na(`2 YEAR VISIT - Date of visit`) |  -->
<!--       !is.na(`3 YEAR VISIT - Date of visit`)] %>%  -->
<!--   .[, followup_5y :=  -->
<!--       !is.na(`5 YEAR VISIT - Date of visit`) |  -->
<!--       !is.na(`6 YEAR VISIT - Date of visit`)] -->
<!-- ``` -->

<!-- ### Filters -->

<!-- ```{r echo=FALSE} -->
<!-- data_set %<>% -->
<!--   .[followup_2y==TRUE] %>% -->
<!--   .[`st1. Date of Stage` %>% as.Date() < as.Date('2016-6-1')] -->
<!-- ``` -->

<!-- ```{r, echo=FALSE} -->
<!-- patients_all <- data_set[, `Code of the patient` %>% unique] -->
<!-- ``` -->

<!-- ```{r, echo=FALSE} -->
<!-- complications_all <- read_excel(xls_path, sheet='Complications') %>% -->
<!--   as.data.table %>%  -->
<!--   .[`Code of the patient` %in% patients_all]  -->

<!-- complications_all[, Category := strsplit( -->
<!--     `Category of the complication`, ":")[[1]][1], -->
<!--     1:nrow(complications_all)] -->
<!-- ``` -->


<!-- ```{r include=FALSE} -->
<!-- patient_2yFU <- data_set[followup_2y==TRUE, `Code of the patient` %>% unique] -->
<!-- patient_2y_5yFU <- data_set[followup_2y==TRUE & followup_5y==TRUE, `Code of the patient` %>% unique] -->
<!-- ``` -->

<!-- ### Major Complications -->

<!-- ```{r, echo=FALSE} -->
<!-- comp_type <- "Major Complication" -->
<!-- complications_all %>% -->
<!--   .[`Code of the patient` %in% patient_2yFU] %>%  -->
<!--   .[`Complication Impact` == comp_type] %>%  -->
<!--   .[`Days since surgery` < 365*2 ] -> -->
<!--   comps_2y -->

<!-- complications_all %>% -->
<!--   .[`Code of the patient` %in% patient_2yFU] %>%  -->
<!--   .[`Days since surgery` < 365*2 ] %>%  -->
<!--   .[, `Code of the patient` %>% uniqueN]-> -->
<!--   elegible_2y -->

<!-- patients_2y <- comps_2y[, `Code of the patient` %>% unique] -->

<!-- complications_all %>% -->
<!--   .[`Code of the patient` %in% patient_2y_5yFU] %>%  -->
<!--   .[`Complication Impact` == comp_type] %>%  -->
<!--   .[`Days since surgery` >= 365*2 ] %>%  -->
<!--   .[`Days since surgery` < 365*5 ] -> -->
<!--   comps_2y_5y -->

<!-- complications_all %>% -->
<!--   .[`Code of the patient` %in% patient_2y_5yFU] %>%  -->
<!--   .[`Days since surgery` >= 365*2 ] %>%  -->
<!--   .[`Days since surgery` < 365*5 ]  %>%  -->
<!--   .[, `Code of the patient` %>% uniqueN] -> -->
<!--   elegible_2y_5y -->

<!-- patients_2y_5y <- comps_2y_5y[, `Code of the patient` %>% unique] -->

<!-- patients_n <- len(patients_all) -->
<!-- patients_2y_n <- len(patients_2y) -->
<!-- patients_2y_5y_n <- len(patients_2y_5y) -->
<!-- p_val <- prop.test(c(patients_2y_n, patients_2y_5y_n), c(elegible_2y, elegible_2y_5y))$p.value -->
<!-- ``` -->

<!-- - Total patients: `r patients_n` -->

<!-- - Complications before 2 years: `r comps_2y[, .N]` -->
<!-- - Elegible patients with 2Y: `r elegible_2y` -->
<!-- - Patients with complications before 2 years: `r patients_2y_n` -->
<!-- - Proportion of patients with complications before 2 years: `r patients_2y_n / elegible_2y` -->

<!-- - Complications between 2y and 5y: `r comps_2y_5y[, .N]` -->
<!-- - Elegible patients with 2Y and 5Y: `r elegible_2y_5y` -->
<!-- - Patients with complications before 5 years: `r patients_2y_5y_n` -->
<!-- - Proportion of patients with complications between 2y and 5y: `r patients_2y_5y_n / elegible_2y_5y` -->

<!-- - p-value testing equality between proportions of complications: `r p_val` -->

<!-- ```{r include=FALSE} -->
<!-- patients_2y_n_260_major <- patients_2y_n -->
<!-- elegible_2y_260_major <- elegible_2y -->
<!-- patients_2y_5y_n_260_major <- patients_2y_5y_n -->
<!-- elegible_2y_5y_260_major <- elegible_2y_5y -->
<!-- ``` -->



<!-- ```{r comment="", echo=FALSE} -->
<!-- major_260 <- complications_all %>% -->
<!--   .[`Complication Impact` == comp_type] %>%  -->
<!--   .[`Days since surgery` < 365*2 ] %>%  -->
<!--   .[, .(pats_n = uniqueN(`Code of the patient`)), Category] -->

<!-- major_260[, prop := pats_n/sum(major_260[, pats_n])] -->
<!-- major_260  -->
<!-- ``` -->


<!-- ### Minor Complications -->

<!-- ```{r, echo=FALSE} -->
<!-- comp_type <- "Minor Complication" -->
<!-- complications_all %>% -->
<!--   .[`Code of the patient` %in% patient_2yFU] %>%  -->
<!--   .[`Complication Impact` == comp_type] %>%  -->
<!--   .[`Days since surgery` < 365*2 ] -> -->
<!--   comps_2y -->

<!-- complications_all %>% -->
<!--   .[`Code of the patient` %in% patient_2yFU] %>%  -->
<!--   .[`Days since surgery` < 365*2 ] %>%  -->
<!--   .[, `Code of the patient` %>% uniqueN]-> -->
<!--   elegible_2y -->

<!-- patients_2y <- comps_2y[, `Code of the patient` %>% unique] -->

<!-- complications_all %>% -->
<!--   .[`Code of the patient` %in% patient_2y_5yFU] %>%  -->
<!--   .[`Complication Impact` == comp_type] %>%  -->
<!--   .[`Days since surgery` >= 365*2 ] %>%  -->
<!--   .[`Days since surgery` < 365*5 ] -> -->
<!--   comps_2y_5y -->

<!-- complications_all %>% -->
<!--   .[`Code of the patient` %in% patient_2y_5yFU] %>%  -->
<!--   .[`Days since surgery` >= 365*2 ] %>%  -->
<!--   .[`Days since surgery` < 365*5 ]  %>%  -->
<!--   .[, `Code of the patient` %>% uniqueN] -> -->
<!--   elegible_2y_5y -->

<!-- patients_2y_5y <- comps_2y_5y[, `Code of the patient` %>% unique] -->

<!-- patients_n <- len(patients_all) -->
<!-- patients_2y_n <- len(patients_2y) -->
<!-- patients_2y_5y_n <- len(patients_2y_5y) -->
<!-- p_val <- prop.test(c(patients_2y_n, patients_2y_5y_n), c(elegible_2y, elegible_2y_5y))$p.value -->
<!-- ``` -->

<!-- - Total patients: `r patients_n` -->

<!-- - Complications before 2 years: `r comps_2y[, .N]` -->
<!-- - Elegible patients with 2Y: `r elegible_2y` -->
<!-- - Patients with complications before 2 years: `r patients_2y_n` -->
<!-- - Proportion of patients with complications before 2 years: `r patients_2y_n / elegible_2y` -->

<!-- - Complications between 2y and 5y: `r comps_2y_5y[, .N]` -->
<!-- - Elegible patients with 2Y and 5Y: `r elegible_2y_5y` -->
<!-- - Patients with complications before 5 years: `r patients_2y_5y_n` -->
<!-- - Proportion of patients with complications between 2y and 5y: `r patients_2y_5y_n / elegible_2y_5y` -->

<!-- - p-value testing equality between proportions of complications: `r p_val` -->

<!-- ```{r include=FALSE} -->
<!-- patients_2y_n_260_minor <- patients_2y_n -->
<!-- elegible_2y_260_minor <- elegible_2y -->
<!-- patients_2y_5y_n_260_minor <- patients_2y_5y_n -->
<!-- elegible_2y_5y_260_minor <- elegible_2y_5y -->
<!-- ``` -->



<!-- ```{r comment="", echo=FALSE} -->
<!-- minor_260 <- complications_all %>% -->
<!--   .[`Complication Impact` == comp_type] %>%  -->
<!--   .[`Days since surgery` < 365*2 ] %>%  -->
<!--   .[, .(pats_n = uniqueN(`Code of the patient`)), Category] -->

<!-- minor_260[, prop := pats_n/sum(minor_260[, pats_n])] -->
<!-- minor_260  -->
<!-- ``` -->



# Comparations

## All vs nondepuy 2Y


### Major

P-value: Proportion 2y depuy vs non depuy

```{r include=FALSE}
prop.test(c(patients_2y_n_dp_major, patients_2y_n_nondp_major), c(elegible_2y_dp_major, elegible_2y_nondp_major))$p.value
```


```{r comment="", echo=FALSE, warning=FALSE}
t1 <- major_all
t2 <- major_nondp

t1_n <- sum(t1[, pats_n])
t2_n <- sum(t2[, pats_n])

results <- list()
for( name in intersect(t1[, Category], t2[, Category])){
  t1_val_n <- as.numeric(t1[Category==name, pats_n])
  t2_val_n <- as.numeric(t2[Category==name, pats_n])
  results[[name]] <- prop.test(
    c(t1_val_n, t2_val_n),
    c(t1_n, t2_n),
  )$p.val
}

data.frame(
  complication = names(results),
  p_val = unlist(results) %>% as.numeric
)
```

### Minor

P-value: Proportion before 2y vs non depuy

```{r include=FALSE}
prop.test(c(patients_2y_n_dp_minor, patients_2y_n_nondp_minor), c(elegible_2y_dp_minor, elegible_2y_nondp_minor))$p.value
```


```{r comment="", echo=FALSE, warning=FALSE}
t1 <- minor_all
t2 <- minor_nondp

t1_n <- sum(t1[, pats_n])
t2_n <- sum(t2[, pats_n])

results <- list()
for( name in intersect(t1[, Category], t2[, Category])){
  t1_val_n <- as.numeric(t1[Category==name, pats_n])
  t2_val_n <- as.numeric(t2[Category==name, pats_n])
  results[[name]] <- prop.test(
    c(t1_val_n, t2_val_n),
    c(t1_n, t2_n),
  )$p.val
}

data.frame(
  complication = names(results),
  p_val = unlist(results) %>% as.numeric
)
```

## All vs nondepuy between 2Y and 5Y


### Major

P-value: Proportion 2y and 5Y depuy vs non depuy

```{r include=FALSE}
prop.test(c(patients_2y_5y_n_dp_major, patients_2y_5y_n_nondp_major), c(elegible_2y_5y_dp_major, elegible_2y_5y_nondp_major))$p.value
```


```{r comment="", echo=FALSE, warning=FALSE}
t1 <- major_all_25
t2 <- major_nondp_25

t1_n <- sum(t1[, pats_n])
t2_n <- sum(t2[, pats_n])

results <- list()
for( name in intersect(t1[, Category], t2[, Category])){
  t1_val_n <- as.numeric(t1[Category==name, pats_n])
  t2_val_n <- as.numeric(t2[Category==name, pats_n])
  results[[name]] <- prop.test(
    c(t1_val_n, t2_val_n),
    c(t1_n, t2_n),
  )$p.val
}

data.frame(
  complication = names(results),
  p_val = unlist(results) %>% as.numeric
)
```

### Minor

P-value: Proportion between 2y and 5y depuy vs non depuy

```{r include=FALSE}
prop.test(c(patients_2y_5y_n_dp_minor, patients_2y_5y_n_nondp_minor), c(elegible_2y_5y_dp_minor, elegible_2y_5y_nondp_minor))$p.value
```


```{r comment="", echo=FALSE, warning=FALSE}
t1 <- minor_all_25
t2 <- minor_nondp_25

t1_n <- sum(t1[, pats_n])
t2_n <- sum(t2[, pats_n])

results <- list()
for( name in intersect(t1[, Category], t2[, Category])){
  t1_val_n <- as.numeric(t1[Category==name, pats_n])
  t2_val_n <- as.numeric(t2[Category==name, pats_n])
  results[[name]] <- prop.test(
    c(t1_val_n, t2_val_n),
    c(t1_n, t2_n),
  )$p.val
}

data.frame(
  complication = names(results),
  p_val = unlist(results) %>% as.numeric
)
```


<!-- ## Before 2YFU vs nondepuy -->

<!-- ### Major -->
<!-- ```{r comment="", echo=FALSE, warning=FALSE} -->
<!-- t1 <- major_260 -->
<!-- t2 <- major_nondepuy -->

<!-- t1_n <- sum(t1[, pats_n]) -->
<!-- t2_n <- sum(t2[, pats_n]) -->

<!-- results <- list() -->
<!-- for( name in intersect(t1[, Category], t2[, Category])){ -->
<!--   t1_val_n <- as.numeric(t1[Category==name, pats_n]) -->
<!--   t2_val_n <- as.numeric(t1[Category==name, pats_n]) -->
<!--   results[[name]] <- prop.test( -->
<!--     c(t1_val_n, t2_val_n), -->
<!--     c(t1_n, t2_n), -->
<!--   )$p.val -->
<!-- } -->

<!-- data.frame( -->
<!--   complication = names(results), -->
<!--   p_val = unlist(results) %>% as.numeric -->
<!-- ) -->
<!-- ``` -->

<!-- ### Minor -->
<!-- ```{r comment="", echo=FALSE, warning=FALSE} -->
<!-- t1 <- minor_260 -->
<!-- t2 <- minor_nondepuy -->

<!-- t1_n <- sum(t1[, pats_n]) -->
<!-- t2_n <- sum(t2[, pats_n]) -->

<!-- results <- list() -->
<!-- for( name in intersect(t1[, Category], t2[, Category])){ -->
<!--   t1_val_n <- as.numeric(t1[Category==name, pats_n]) -->
<!--   t2_val_n <- as.numeric(t1[Category==name, pats_n]) -->
<!--   results[[name]] <- prop.test( -->
<!--     c(t1_val_n, t2_val_n), -->
<!--     c(t1_n, t2_n), -->
<!--   )$p.val -->
<!-- } -->

<!-- data.frame( -->
<!--   complication = names(results), -->
<!--   p_val = unlist(results) %>% as.numeric -->
<!-- ) -->
<!-- ``` -->

