---
title: "5y quality life analysis"
output:
  pdf_document: default
  html_document: default
always_allow_html: true
---

  
```{r setup, include=FALSE}
knitr::opts_knit$set(
  echo = FALSE, 
  root.dir=normalizePath('../'),
  warning=FALSE, 
  comment="",
  message=FALSE
)
```


```{r echo=TRUE}
xls_path <- '../../data/ESSG Extraction_DEC_OP_ NON DePuy v7.xlsx'
```

```{r warning=FALSE, echo=FALSE, include=FALSE}
library(stringr)
library(ggplot2)
library(zeallot)
library(gridExtra)
library(DiagrammeR)

source('five_years/five_years-utils.R')

ncols_plots <- 2

outcomes <- c(
  '5Y. ODI - Score (%)', '5Y. SRS22 - SRS Subtotal score', '5Y. SF36 - PCS', '5Y. SF36 - MCS',
  '5Y. SRS22 - Satisfaction with management'
)

c(data_set_0, predictive_vars, .) %<-% get_data(xls_path, clean=FALSE)
data_set <- data_set_0 %>% copy

complications <- read_excel(xls_path, sheet='Complications') %>%
  as.data.table %>%
  .[`Complication Impact` == 'Major Complication'] 

reinterventions <- read_excel(xls_path, sheet = "Revision surgery") %>%
  data.table 

data_set_0 %>% 
  .[, .(
    `Code of the patient`, 
    stage_date=`st1. Date of Stage`
  )]  %>% 
  rbind(
    reinterventions %>% 
      .[, .(
        `Code of the patient`, 
        stage_date=`st1. Date of Stage`
      )]    
  ) %>% 
  .[!is.na(stage_date)] %>% 
  .[, diff_years:=difftime(stage_date, min(stage_date), units = "days")/365, 
    `Code of the patient`] %>% 
  .[diff_years > 0] ->
  reinterventions


demographics <- read_yaml('five_years/demographic.yml')
demographics_all <- demographics %>% unlist


outcomes %>% 
  lapply(. %>% str_replace_all('5', '2')) ->
  outcomes_2y
names(outcomes_2y) <- outcomes

outcomes %>% 
  lapply(. %>% str_replace_all('5', '3')) ->
  outcomes_3y
names(outcomes_3y) <- outcomes

outcomes %>% 
  lapply(. %>% str_replace_all('5', '6')) ->
  outcomes_6y
names(outcomes_6y) <- outcomes

outcomes %>% 
  sapply(. %>% get_base_outcome(first_visit=TRUE)) ->
  base_outcomes 

for( outcome in names(outcomes_6y)){
  outcome_6y <- outcomes_6y[[outcome]]
  outcome_2y <- outcomes_2y[[outcome]]
  outcome_3y <- outcomes_3y[[outcome]]
  data_set %<>%
    .[is.na(get(outcome)), c(outcome) := get(outcome_6y)] %>% 
    .[is.na(get(outcome_2y)), c(outcome_2y) := get(outcome_3y)]
}

radio_6w <- demographics$radiologic %>% 
  sapply(function(x) '6W. {x}' %>% f)

# outcome_2y <- outcomes_2y[[1]]
# outcome <- outcomes[[1]]

if( 'Major curve Cobb angle' %in% colnames(data_set)){
  setnames(data_set, 
    "Major curve Cobb angle", "Static Major curve Cobb angle")
}

study_vars <- c(
  outcomes, outcomes_2y %>% unlist, 
  demographics_all, base_outcomes, 
  radio_6w, 
  'Code of the patient', 
  'Site', 
  'Study', 
  'Vital status', 
  'st1. Date of Stage', 
  '2 YEAR VISIT - Date of visit',
  '3 YEAR VISIT - Date of visit',
  '5 YEAR VISIT - Date of visit',
  '6 YEAR VISIT - Date of visit'
) %>% unique
data_set %<>% 
  .[, .SD, .SDcols=study_vars] 
```

### Filters
```{r warning=FALSE }
# discarded_patients <- readLines('five_years/discarded_patients')

data_set %<>% 
  .[, followup_2y := 
      !is.na(`2 YEAR VISIT - Date of visit`) | 
      !is.na(`3 YEAR VISIT - Date of visit`) ] %>% 
  .[, followup_5y := 
      !is.na(`5 YEAR VISIT - Date of visit`) | 
      !is.na(`6 YEAR VISIT - Date of visit`) ]
```

```{r echo=TRUE}
# data_set %<>%
#   .[followup_2y==TRUE] %>%
#   .[`st1. Date of Stage` %>% as.Date() < as.Date('2016-6-1')]
```

Total Patients for the analysis: `r data_set[, .N]`

```{r echo=FALSE}
data_set %<>% 
  .[, followup_2y := ifelse(followup_2y == TRUE, 'has_followup', 'no_followup')] %>% 
  .[, followup_5y := ifelse(followup_5y == TRUE, 'has_followup', 'no_followup')] 

patients_all <- data_set[, `Code of the patient` %>% unique]
complications %<>% .[`Code of the patient` %in% patients_all]
patiens_complications <- complications[, `Code of the patient`] %>% unique

data_set %>% 
  .[, had_major_complications := 'No'] %>% 
  .[`Code of the patient` %in% patiens_complications, 
    had_major_complications := 'Yes'] 
```


```{r echo=FALSE}
reinterventions %>%  
  .[diff_years < 5] %>% 
  .[, `Code of the patient`] ->
  patients_reinterventions 

data_set %>% 
  .[, had_reinterventions := 'No'] %>% 
  .[`Code of the patient` %in% patients_reinterventions, 
    had_reinterventions := 'Yes']

```


```{r echo=FALSE}
grViz('
digraph rmarkdown {

  graph [
    rankdir = UD
  ]
  
  node [
    shape=circle,
    fixedsize=true,
    width=1.2,
    style=filled,
    fillcolor=aquamarine2,
    fontsize=15
    ]

 
  D[label="Demographic"]
  R[label="Radiologic\n(Deformity)"]
  O[label="Outcome"]
  
  D -> R 
  D -> O
  R -> O
  
}                  
')
```

```{r echo=FALSE, comment=""}
demographics %>% as.yaml %>% cat
get_model_info <- . %>% summary %>% coefficients %>% round(3)
```

# Scores

```{r echo=FALSE}
outcome <- outcomes[1]
htmltools::h1(outcome)
```


```{r echo=FALSE, message=FALSE, warning=FALSE}
data_set[, 
  .SD, 
  .SDcols=c(get_base_outcome(outcome, first_visit=TRUE), outcomes_2y[[outcome]], outcome)
] %>% 
  melt() %>% 
  ggplot(aes(variable, value)) +
  geom_boxplot() +
  theme(axis.text.x = element_text(angle = 10, vjust = 0.5, hjust=1))
```

<!-- ```{r echo=FALSE, include=FALSE} -->
<!-- demo_plots <- plot_scores(data_set, outcome, demographics_all) -->
<!-- ``` -->

<!-- ```{r echo=FALSE, message=FALSE, fig.height=30, fig.width=10, warning=FALSE} -->
<!-- do.call("grid.arrange", c(demo_plots, ncol=ncols_plots)) -->
<!-- ``` -->


```{r echo=FALSE, comment=""}
outcome_2y <- outcomes_2y[[outcome]]
base_outcome <- base_outcomes[[outcome]]
htmltools::h3(base_outcome)
```

### Basic stats
```{r echo=FALSE, comment=""}
data_set[, 
  lapply(.SD, . %>% mean(na.rm=TRUE)), 
  .SDcols = c(base_outcome, outcome_2y, outcome)
] %>% 
  rbind(
    data_set[, 
      lapply(.SD, . %>% sd(na.rm=TRUE)), 
      .SDcols = c(base_outcome, outcome_2y, outcome)
    ]
  ) %>% 
  data.table(type=c('Mean', 'Sd'),.)  
```


### t-test mean comparison p-values
```{r echo=FALSE, comment=""}
outcome_vals <- data_set[, get(outcome)]
outcome_2y_vals <- data_set[, get(outcome_2y)]
outcome_base_vals <- data_set[, get(base_outcome)]
comp_base_5 <- t.test(outcome_vals, outcome_base_vals)$p.val %>% round(5)
comp_2_5 <- t.test(outcome_vals, outcome_2y_vals)$p.val %>% round(5)
comp_base_2 <- t.test(outcome_base_vals, outcome_2y_vals)$p.val %>% round(5)

data.table(
  type=c('base vs 5', '2 vs 5', 'base vs 2'), 
  c(comp_base_5, comp_2_5, comp_base_2))
```


### 5 Years Gain Gain (odi neg / others pos) Factors 
```{r echo=FALSE, comment=""}
base_factors <- basic_factors_5y_gain(data_set, outcome, base_outcome, demographics)
htmltools::h5('Demographics')
base_factors$model_demo %>% print
htmltools::h5('Radiology')
base_factors$model_radio %>% print
htmltools::h5('HRQL')
base_factors$model_quality %>% print
htmltools::h5('Correction Radiology')
base_factors$model_radio_correction %>% print
htmltools::h5('Complications')
base_factors$model_complications %>% print
htmltools::h5('Reinterventions')
base_factors$model_reinterventions %>% print
```


### 5Y vs 2Y Effects
```{r echo=FALSE, comment=""}
models <- variable_effect(data_set, outcome, outcome_2y, demographics)
htmltools::h5('Demographics')
models$demographic %>% print
htmltools::h5('Radiology')
models$radiology %>% print
```


```{r echo=FALSE, comment=""}
outcome <- outcomes[2]
htmltools::h1(outcome)
```


```{r echo=FALSE, message=FALSE, warning=FALSE}

data_set[, 
  .SD, 
  .SDcols=c(get_base_outcome(outcome, first_visit=TRUE), outcomes_2y[[outcome]], outcome)
] %>% 
  melt() %>% 
  ggplot(aes(variable, value)) +
  geom_boxplot() +
  theme(axis.text.x = element_text(angle = 10, vjust = 0.5, hjust=1))
```

<!-- ```{r echo=FALSE, include=FALSE} -->
<!-- demo_plots <- plot_scores(data_set, outcome, demographics_all) -->
<!-- ``` -->


<!-- ```{r echo=FALSE, message=FALSE, fig.height=30, fig.width=10, warning=FALSE} -->
<!-- do.call("grid.arrange", c(demo_plots, ncol=ncols_plots)) -->
<!-- ``` -->


```{r echo=FALSE, comment=""}
outcome_2y <- outcomes_2y[[outcome]]
base_outcome <- base_outcomes[[outcome]]
htmltools::h3(base_outcome)
```

### Basic stats
```{r echo=FALSE, comment=""}
data_set[, 
  lapply(.SD, . %>% mean(na.rm=TRUE)), 
  .SDcols = c(base_outcome, outcome_2y, outcome)
] %>% 
  rbind(
    data_set[, 
      lapply(.SD, . %>% sd(na.rm=TRUE)), 
      .SDcols = c(base_outcome, outcome_2y, outcome)
    ]
  ) %>% 
  data.table(type=c('Mean', 'Sd'),.)  
```


### t-test mean comparison p-values
```{r echo=FALSE, comment=""}
outcome_vals <- data_set[, get(outcome)]
outcome_2y_vals <- data_set[, get(outcome_2y)]
outcome_base_vals <- data_set[, get(base_outcome)]
comp_base_5 <- t.test(outcome_vals, outcome_base_vals)$p.val %>% round(5)
comp_2_5 <- t.test(outcome_vals, outcome_2y_vals)$p.val %>% round(5)
comp_base_2 <- t.test(outcome_base_vals, outcome_2y_vals)$p.val %>% round(5)

data.table(
  type=c('base vs 5', '2 vs 5', 'base vs 2'), 
  c(comp_base_5, comp_2_5, comp_base_2))
```


### 5 Years Gain Gain (odi neg / others pos) Factors 
```{r echo=FALSE, comment=""}
base_factors <- basic_factors_5y_gain(data_set, outcome, base_outcome, demographics)
htmltools::h5('Demographics')
base_factors$model_demo %>% print
htmltools::h5('Radiology')
base_factors$model_radio %>% print
htmltools::h5('HRQL')
base_factors$model_quality %>% print
htmltools::h5('Correction Radiology')
base_factors$model_radio_correction %>% print
htmltools::h5('Complications')
base_factors$model_complications %>% print
htmltools::h5('Reinterventions')
base_factors$model_reinterventions %>% print
```


### 5Y vs 2Y Effects
```{r echo=FALSE, comment=""}
models <- variable_effect(data_set, outcome, outcome_2y, demographics)
htmltools::h5('Demographics')
models$demographic %>% print
htmltools::h5('Radiology')
models$radiology %>% print
```


```{r echo=FALSE}
outcome <- outcomes[3]
htmltools::h1(outcome)
```


```{r echo=FALSE, message=FALSE, warning=FALSE}

data_set[, 
  .SD, 
  .SDcols=c(get_base_outcome(outcome, first_visit=TRUE), outcomes_2y[[outcome]], outcome)
] %>% 
  melt() %>% 
  ggplot(aes(variable, value)) +
  geom_boxplot() +
  theme(axis.text.x = element_text(angle = 10, vjust = 0.5, hjust=1))
```

<!-- ```{r echo=FALSE, include=FALSE} -->
<!-- demo_plots <- plot_scores(data_set, outcome, demographics_all) -->
<!-- ``` -->


<!-- ```{r echo=FALSE, message=FALSE, fig.height=30, fig.width=10, warning=FALSE} -->
<!-- do.call("grid.arrange", c(demo_plots, ncol=ncols_plots)) -->
<!-- ``` -->

```{r echo=FALSE, comment=""}
outcome_2y <- outcomes_2y[[outcome]]
base_outcome <- base_outcomes[[outcome]]
htmltools::h3(base_outcome)
```

### Basic stats
```{r echo=FALSE, comment=""}
data_set[, 
  lapply(.SD, . %>% mean(na.rm=TRUE)), 
  .SDcols = c(base_outcome, outcome_2y, outcome)
] %>% 
  rbind(
    data_set[, 
      lapply(.SD, . %>% sd(na.rm=TRUE)), 
      .SDcols = c(base_outcome, outcome_2y, outcome)
    ]
  ) %>% 
  data.table(type=c('Mean', 'Sd'),.)  
```


### t-test mean comparison p-values
```{r echo=FALSE, comment=""}
outcome_vals <- data_set[, get(outcome)]
outcome_2y_vals <- data_set[, get(outcome_2y)]
outcome_base_vals <- data_set[, get(base_outcome)]
comp_base_5 <- t.test(outcome_vals, outcome_base_vals)$p.val %>% round(5)
comp_2_5 <- t.test(outcome_vals, outcome_2y_vals)$p.val %>% round(5)
comp_base_2 <- t.test(outcome_base_vals, outcome_2y_vals)$p.val %>% round(5)

data.table(
  type=c('base vs 5', '2 vs 5', 'base vs 2'), 
  c(comp_base_5, comp_2_5, comp_base_2))
```



### 5 Years Gain Gain (odi neg / others pos) Factors 
```{r echo=FALSE, comment=""}
base_factors <- basic_factors_5y_gain(data_set, outcome, base_outcome, demographics)
htmltools::h5('Demographics')
base_factors$model_demo %>% print
htmltools::h5('Radiology')
base_factors$model_radio %>% print
htmltools::h5('HRQL')
base_factors$model_quality %>% print
htmltools::h5('Correction Radiology')
base_factors$model_radio_correction %>% print
htmltools::h5('Complications')
base_factors$model_complications %>% print
htmltools::h5('Reinterventions')
base_factors$model_reinterventions %>% print
```


### 5Y vs 2Y Effects
```{r echo=FALSE, comment=""}
models <- variable_effect(data_set, outcome, outcome_2y, demographics)
htmltools::h5('Demographics')
models$demographic %>% print
htmltools::h5('Radiology')
models$radiology %>% print
```



```{r echo=FALSE}
outcome <- outcomes[4]
htmltools::h1(outcome)
```


```{r echo=FALSE, message=FALSE, warning=FALSE}

data_set[, 
  .SD, 
  .SDcols=c(get_base_outcome(outcome, first_visit=TRUE), outcomes_2y[[outcome]], outcome)
] %>% 
  melt() %>% 
  ggplot(aes(variable, value)) +
  geom_boxplot() +
  theme(axis.text.x = element_text(angle = 10, vjust = 0.5, hjust=1))
```

<!-- ```{r echo=FALSE, include=FALSE} -->
<!-- demo_plots <- plot_scores(data_set, outcome, demographics_all) -->
<!-- ``` -->


<!-- ```{r echo=FALSE, message=FALSE, fig.height=30, fig.width=10, warning=FALSE} -->
<!-- do.call("grid.arrange", c(demo_plots, ncol=ncols_plots)) -->
<!-- ``` -->

```{r echo=FALSE, comment=""}
outcome_2y <- outcomes_2y[[outcome]]
base_outcome <- base_outcomes[[outcome]]
htmltools::h3(base_outcome)
```

### Basic stats
```{r echo=FALSE, comment=""}
data_set[, 
  lapply(.SD, . %>% mean(na.rm=TRUE)), 
  .SDcols = c(base_outcome, outcome_2y, outcome)
] %>% 
  rbind(
    data_set[, 
      lapply(.SD, . %>% sd(na.rm=TRUE)), 
      .SDcols = c(base_outcome, outcome_2y, outcome)
    ]
  ) %>% 
  data.table(type=c('Mean', 'Sd'),.)  
```


### t-test mean comparison p-values
```{r echo=FALSE, comment=""}
outcome_vals <- data_set[, get(outcome)]
outcome_2y_vals <- data_set[, get(outcome_2y)]
outcome_base_vals <- data_set[, get(base_outcome)]
comp_base_5 <- t.test(outcome_vals, outcome_base_vals)$p.val %>% round(5)
comp_2_5 <- t.test(outcome_vals, outcome_2y_vals)$p.val %>% round(5)
comp_base_2 <- t.test(outcome_base_vals, outcome_2y_vals)$p.val %>% round(5)

data.table(
  type=c('base vs 5', '2 vs 5', 'base vs 2'), 
  c(comp_base_5, comp_2_5, comp_base_2))
```


### 5 Years Gain Gain (odi neg / others pos) Factors 
```{r echo=FALSE, comment=""}
base_factors <- basic_factors_5y_gain(data_set, outcome, base_outcome, demographics)
htmltools::h5('Demographics')
base_factors$model_demo %>% print
htmltools::h5('Radiology')
base_factors$model_radio %>% print
htmltools::h5('HRQL')
base_factors$model_quality %>% print
htmltools::h5('Correction Radiology')
base_factors$model_radio_correction %>% print
htmltools::h5('Complications')
base_factors$model_complications %>% print
htmltools::h5('Reinterventions')
base_factors$model_reinterventions %>% print
```


### 5Y vs 2Y Effects
```{r echo=FALSE, comment=""}
models <- variable_effect(data_set, outcome, outcome_2y, demographics)
htmltools::h5('Demographics')
models$demographic %>% print
htmltools::h5('Radiology')
models$radiology %>% print
```


```{r echo=FALSE}
outcome <- outcomes[5]
htmltools::h1(outcome)
```


```{r echo=FALSE, message=FALSE, warning=FALSE}

data_set[, 
  .SD, 
  .SDcols=c(get_base_outcome(outcome, first_visit=TRUE), outcomes_2y[[outcome]], outcome)
] %>% 
  melt() %>% 
  ggplot(aes(variable, value)) +
  geom_boxplot() +
  theme(axis.text.x = element_text(angle = 10, vjust = 0.5, hjust=1))
```

<!-- ```{r echo=FALSE, include=FALSE} -->
<!-- demo_plots <- plot_scores(data_set, outcome, demographics_all) -->
<!-- ``` -->


<!-- ```{r echo=FALSE, message=FALSE, fig.height=30, fig.width=10, warning=FALSE} -->
<!-- do.call("grid.arrange", c(demo_plots, ncol=ncols_plots)) -->
<!-- ``` -->

```{r echo=FALSE, comment=""}
outcome_2y <- outcomes_2y[[outcome]]
base_outcome <- base_outcomes[[outcome]]
htmltools::h3(base_outcome)
```

### Basic stats
```{r echo=FALSE, comment=""}
data_set[, 
  lapply(.SD, . %>% mean(na.rm=TRUE)), 
  .SDcols = c(base_outcome, outcome_2y, outcome)
] %>% 
  rbind(
    data_set[, 
      lapply(.SD, . %>% sd(na.rm=TRUE)), 
      .SDcols = c(base_outcome, outcome_2y, outcome)
    ]
  ) %>% 
  data.table(type=c('Mean', 'Sd'),.)  
```


### t-test mean comparison p-values
```{r echo=FALSE, comment=""}
outcome_vals <- data_set[, get(outcome)]
outcome_2y_vals <- data_set[, get(outcome_2y)]
outcome_base_vals <- data_set[, get(base_outcome)]
comp_base_5 <- t.test(outcome_vals, outcome_base_vals)$p.val %>% round(5)
comp_2_5 <- t.test(outcome_vals, outcome_2y_vals)$p.val %>% round(5)
comp_base_2 <- t.test(outcome_base_vals, outcome_2y_vals)$p.val %>% round(5)

data.table(
  type=c('base vs 5', '2 vs 5', 'base vs 2'), 
  c(comp_base_5, comp_2_5, comp_base_2))
```


### 5 Years Gain Gain (odi neg / others pos) Factors 
```{r echo=FALSE, comment=""}
base_factors <- basic_factors_5y_gain(data_set, outcome, base_outcome, demographics)
htmltools::h5('Demographics')
base_factors$model_demo %>% print
htmltools::h5('Radiology')
base_factors$model_radio %>% print
htmltools::h5('HRQL')
base_factors$model_quality %>% print
htmltools::h5('Correction Radiology')
base_factors$model_radio_correction %>% print
htmltools::h5('Complications')
base_factors$model_complications %>% print
htmltools::h5('Reinterventions')
base_factors$model_reinterventions %>% print
```


### 5Y vs 2Y Effects
```{r echo=FALSE, comment=""}
models <- variable_effect(data_set, outcome, outcome_2y, demographics)
htmltools::h5('Demographics')
models$demographic %>% print
htmltools::h5('Radiology')
models$radiology %>% print
```
