---
title: "Reinterventions exploration"
output:
  html_document: default
  pdf_document: default
always_allow_html: yes
---

```{r setup, include=FALSE}
knitr::opts_knit$set(
  echo = FALSE, 
  warning = FALSE,
  root.dir=normalizePath('../../'),
  comment=""
)
```

```{r warning=FALSE, include=FALSE}
library(readxl)
library(magrittr)
library(data.table)
library(stringr)
library(yaml)
library(zeallot)
library(DT)

source('code/basic.R')
source('code/utils.R')
source('code/reintervention/reinterventions-util.R')

c(time_evolution, complications, category_los, clinical_data) %<-% get_data()
controlling_vars <- read_yaml('code/reintervention/controling_vars.yml')
```


```{r echo=FALSE}
xls_path <- 'data/ESSG extraction December 2020 - DEF.xlsx'
revision_0 <- read_excel(xls_path, sheet = "Revision surgeries") %>% 
  data.table 
complications_0 <- read_excel(xls_path, sheet = "Complications") %>% 
  data.table 
```

# Controling Variables

```{r comment=''}
cat(controlling_vars %>% as.yaml())
```


```{r echo=FALSE}
y_ <- 5
outcomes <- c(
  "{y_}Y. ODI - Score (%)" %>% f, 
  "{y_}Y. SRS22 - SRS Subtotal score" %>% f,
  "{y_}Y. SF36 - MCS" %>% f,
  "{y_}Y. SF36 - PCS" %>% f
)

outcomes %>% 
  lapply(. %>% get_base_outcome(first_visit=TRUE)) ->
  base_outcomes
names(base_outcomes) <- outcomes

index_surgeries <- clinical_data[, `Surgery number`] %>% unique
valid_patients <-  clinical_data[, `Code of the patient`] %>% unique
```

Definition of final_status
```{r}
get_surgery_status <- function(status){
  final_status <- 'Resolved without sequelae'
  if( 'Not resolved' %in% status){
    final_status <- 'Not resolved or with sequelae'
  }else if('Resolved with sequelae' %in% status){
    final_status <- 'Not resolved or with sequelae'
  }
  final_status
}
```

# Impact of final status and number of reinterventions associated to an index surgery in `r y_`Y HRQL Gain
```{r}
index_dates <- clinical_data[, .(`Code of the patient`, `st1. Date of Stage 1`)]

complications_0 %>% 
  merge(index_dates,  by='Code of the patient') %>% 
  .[, diff_years:=difftime(`Date of Reoperation`, `st1. Date of Stage 1`, units = "days")/365] %>% 
  .[diff_years < y_] %>% 
  .[`Code of the patient` %in% valid_patients] %>%
  .[`Reoperation Due to Complication` == 'Yes'] %>% 
  .[!is.na(`Date of Reoperation`)] %>% 
  .[, .(
    final_status = get_surgery_status(`Status of the complication`), 
    reinterventions = `Date of Reoperation` %>% uniqueN), 
    .(`Complication associated to surgery`, `Code of the patient` )] ->
  complicated_surgeries

complicated_surgeries_n <- complicated_surgeries[, `Complication associated to surgery`] %>% uniqueN

complicated_surgeries %<>% .[`Complication associated to surgery` %in% index_surgeries]
complicated_surgeries_n_index <- complicated_surgeries[, `Complication associated to surgery`] %>% uniqueN
```

- Surgeries with complications before `r y_`y with valid patients: `r complicated_surgeries_n`
- Index surgeries with complications before `r y_`y with valid patients: `r complicated_surgeries_n_index`
- Valid patients: `r valid_patients %>% len`

```{r echo=FALSE, comment=""}
complicated_surgeries[, .N, final_status]
```


```{r echo=FALSE}
vars_ <- c(
  controlling_vars,
  outcomes,
  base_outcomes %>% unlist,
  'Code of the patient'
) %>% unique


clinical_data %>% 
  .[, .SD, .SDcols=vars_] %>% 
  merge(
    complicated_surgeries, 
    by='Code of the patient', 
    all.x=TRUE) %>% 
  .[, `Complication associated to surgery` := NULL] %>%
  .[, `Code of the patient` := NULL] %>% 
  .[is.na(final_status), final_status :='no complication'] %>% 
  .[is.na(reinterventions), reinterventions := 0] ->
  index_data_
```

```{r echo=FALSE}
lm_vars_ <- c(
  controlling_vars, 
  'outcome_gain' , 
  'reinterventions',
  'final_status'
)

formula <- 'outcome_gain ~ . '
```


```{r comment="", echo=FALSE}
outcome <- outcomes[1]
base_outcome <- base_outcomes[[outcome]]

htmltools::h3(outcome)

index_data_ %>% 
  copy %>% 
  .[, outcome_gain := get(outcome) - get(base_outcome)] %>% 
  .[, .SD, .SDcols = lm_vars_] %>% 
  lm(formula, data=.) %>% summary %>% coefficients %>% .[, c(1, 4)] %>% round(5)
```


```{r comment="", echo=FALSE}
outcome <- outcomes[2]
base_outcome <- base_outcomes[[outcome]]

htmltools::h3(outcome)

index_data_ %>% 
  copy %>% 
  .[, outcome_gain := get(outcome) - get(base_outcome)] %>% 
  .[, .SD, .SDcols = lm_vars_] %>% 
  lm(formula, data=.) %>% summary %>% coefficients %>% .[, c(1, 4)] %>% round(5)
```

```{r comment="", echo=FALSE}
outcome <- outcomes[3]
base_outcome <- base_outcomes[[outcome]]

htmltools::h3(outcome)

index_data_ %>% 
  copy %>% 
  .[, outcome_gain := get(outcome) - get(base_outcome)] %>% 
  .[, .SD, .SDcols = lm_vars_] %>% 
  lm(formula, data=.) %>% summary %>% coefficients %>% .[, c(1, 4)] %>% round(5)
```

```{r comment="", echo=FALSE}
outcome <- outcomes[4]
base_outcome <- base_outcomes[[outcome]]

htmltools::h3(outcome)

index_data_ %>% 
  copy %>% 
  .[, outcome_gain := get(outcome) - get(base_outcome)] %>% 
  .[, .SD, .SDcols = lm_vars_] %>% 
  lm(formula, data=.) %>% summary %>% coefficients %>% .[, c(1, 4)] %>% round(5)
```