---
title: "Reinterventions exploration"
output:
  html_document: default
  pdf_document: default
always_allow_html: yes
---

```{r setup, include=FALSE}
knitr::opts_knit$set(
  echo = FALSE, 
  warning = FALSE,
  root.dir=normalizePath('../../')
)
```

```{r warning=FALSE, include=FALSE}
library(readxl)
library(magrittr)
library(data.table)
library(stringr)
library(yaml)
library(zeallot)

source('code/basic.R')
source('code/utils.R')
source('code/reintervention/reinterventions-util.R')

c(time_evolution, complications, category_los, clinical_data) %<-% get_data()

```


# Proportion of reinterventions


## Patients with 5y FU, reinterventions
Notes: 
- reintervention means that at least has that number of reinterventions



#### all reinterventions
```{r echo=FALSE}
patients_5yfu <- clinical_data %>% 
  .[followup_5y==TRUE] %>% 
  .[, `Code of the patient`]

time_evolution %>% 
  .[patient_id %in% patients_5yfu] %>% 
  .[, .(N=.N), reintervention] %>% 
  .[, prop := round(N/sum(N), 3)*100] %>% 
  print

```

#### reinterventions before 5y
```{r echo=FALSE}
patients_5yfu <- clinical_data %>% 
  .[followup_5y==TRUE] %>% 
  .[, `Code of the patient`]

time_evolution %>% 
  .[diff_years < 5] %>% 
  .[patient_id %in% patients_5yfu] %>% 
  .[, .(N=.N), reintervention] %>% 
  .[, prop := round(N/sum(N), 3)*100] %>% 
  print

```

```{r echo=FALSE}
patients_5yfu <- clinical_data %>% 
  .[followup_5y==TRUE] %>% 
  .[, `Code of the patient`]
clinical_data %<>% .[`Code of the patient` %in% patients_5yfu]
category_los %<>% .[patient_id %in% patients_5yfu]
time_evolution %<>% .[patient_id %in% patients_5yfu]
complications %<>% .[patient_id %in% patients_5yfu]
```



The analysis follows with 5Y FU. Number of patients `r clinical_data[, .N]`

# Proportion of SICU transfers

```{r warning=FALSE, echo=FALSE, fig.height=3.5}

time_evolution %>% 
  .[, .(condition=(sicu_transferred == 'Yes'), reintervention)] %>% 
  .[, .(
    prop=mean(condition) %>% round(3),
    N=.N),
    reintervention] %>% 
  .[, sd:=sqrt(prop*(1-prop)/N) %>% round(3)] ->
  table_info
print(table_info)

time_evolution %>% 
  .[, .(condition=(sicu_transferred == 'Yes'), reintervention)] %>% 
  plot_evolution('transferred to SICU') ->
  evol_res

print(evol_res$res_plot)
print(evol_res$res_lm)
```


# Evolution of surgeries

```{r warning=FALSE, echo=FALSE, fig.height=4, comment=""}


time_evolution %>% 
  .[, .(condition=co3==1, reintervention)] %>% 
  plot_evolution('3CO') ->
  evol_res

print(evol_res$res_plot)
print(evol_res$res_lm)

time_evolution %>% 
  .[, .(condition=(`Implant removal` == 'Yes'), reintervention)] %>% 
  plot_evolution('Implant removal') ->
  evol_res

print(evol_res$res_plot)
print(evol_res$res_lm)

time_evolution %>% 
  .[, .(condition=(`Infection debridement` == 'Yes'), reintervention)] %>% 
  plot_evolution('Infection Debridement') ->
  evol_res

print(evol_res$res_plot)
print(evol_res$res_lm)

time_evolution %>% 
  .[, .(condition=(`Anterior Instrumented Fusion` == 'Yes'), reintervention)] %>% 
  plot_evolution('Anterior Instrumented Fusion') ->
  evol_res

print(evol_res$res_plot)
print(evol_res$res_lm)

time_evolution %>% 
  .[, .(condition=(`Posterior Instrumented Fusion` == 'Yes'), reintervention)] %>% 
  plot_evolution('Posterior Instrumented Fusion') ->
  evol_res

print(evol_res$res_plot)
print(evol_res$res_lm)

time_evolution %>% 
  .[, .(condition=(`Decompression` == 'Yes'), reintervention)] %>% 
  plot_evolution('Decompression') ->
  evol_res

print(evol_res$res_plot)
print(evol_res$res_lm)

time_evolution %>% 
  .[, .(condition=(`Interbody Fusion` == 'Yes'), reintervention)] %>% 
  plot_evolution('Interbody Fusion') ->
  evol_res

print(evol_res$res_plot)
print(evol_res$res_lm)

time_evolution %>% 
  .[, .(condition=(`Osteotomy` == 'Yes'), reintervention)] %>% 
  plot_evolution('Osteotomy') ->
  evol_res

print(evol_res$res_plot)
print(evol_res$res_lm)

time_evolution %>% 
  .[, .(condition=(`Rod change` == 'Yes'), reintervention)] %>% 
  plot_evolution('Rod change') ->
  evol_res

print(evol_res$res_plot)
print(evol_res$res_lm)

time_evolution %>% 
  .[, .(condition=(`Scar revision` == 'Yes'), reintervention)] %>% 
  plot_evolution('Scar revision') ->
  evol_res

print(evol_res$res_plot)
print(evol_res$res_lm)
```


# Hospitalization Time

### Basic stats hospitalization time

```{r echo=FALSE, comment=""}
val_index <- time_evolution[reintervention=='0', hospitalization_time]
val_ur <- time_evolution[reintervention!='0', hospitalization_time]

data.table(type=c('Mean', 'Sd'), 
  index=c(mean(val_index, na.rm=TRUE), sd(val_index, na.rm=TRUE)),
  ur=c(mean(val_ur, na.rm=TRUE), sd(val_ur, na.rm=TRUE))
)
```

### t-test mean comparison p-values index vs ur
```{r echo=FALSE, comment=""}
t.test(val_index, val_ur)$p.val
```


```{r warning=FALSE, echo=FALSE, fig.height=4}
time_evolution %>% 
  ggplot(aes(reintervention, hospitalization_time)) +
  geom_boxplot() +
  ylim(c(0, 250))

time_evolution[, 
  quantile(hospitalization_time, na.rm=TRUE) %>% as.list, 
  reintervention]


time_evolution[, .(hospitalization_time, reintervention)] %>% 
  .[, reintervention := as.numeric(as.character(reintervention))] %>% 
  .[ reintervention <= 3] %>% 
  lm(hospitalization_time~reintervention, data= .) %>% 
  summary %>% 
  coefficients %>% 
  print
```

Note: linear model only up to 3 reinterventions (included)

# Blood Loss

### Basic stats blood loss

```{r echo=FALSE, comment=""}
val_index <- time_evolution[reintervention=='0', blood_loss]
val_ur <- time_evolution[reintervention!='0', blood_loss]

data.table(type=c('Mean', 'Sd'), 
  index=c(mean(val_index, na.rm=TRUE), sd(val_index, na.rm=TRUE)),
  ur=c(mean(val_ur, na.rm=TRUE), sd(val_ur, na.rm=TRUE))
)
```

### t-test mean comparison p-values index vs ur
```{r echo=FALSE, comment=""}
t.test(val_index, val_ur)$p.val
```

```{r echo=FALSE, comment=""}
time_evolution %>% 
  ggplot(aes(blood_loss, fill=reintervention, color=reintervention)) +
  geom_density(alpha=0.1) +
  ggtitle('Blood Loss') +
  xlim(c(0, 3000 ))+
  facet_grid(reintervention~.)

time_evolution[, .(blood_loss, reintervention)] %>% 
  .[, reintervention := as.numeric(as.character(reintervention))] %>% 
  .[ reintervention <= 3] %>% 
  lm(blood_loss~reintervention, data= .) %>% 
  summary %>% 
  coefficients %>% 
  print

time_evolution %>% 
  ggplot(aes(reintervention, blood_loss)) +
  geom_boxplot() +
  ggtitle('Blood Loss')
```

# Surgical Time

### Basic stats surgical time

```{r echo=FALSE, comment=""}
val_index <- time_evolution[reintervention=='0', surgical_time]
val_ur <- time_evolution[reintervention!='0', surgical_time]

data.table(type=c('Mean', 'Sd'), 
  index=c(mean(val_index, na.rm=TRUE), sd(val_index, na.rm=TRUE)),
  ur=c(mean(val_ur, na.rm=TRUE), sd(val_ur, na.rm=TRUE))
)
```

### t-test mean comparison p-values index vs ur
```{r echo=FALSE, comment=""}
t.test(val_index, val_ur)$p.val
```

```{r echo=FALSE, comment=""}
time_evolution %>% 
  ggplot(aes(surgical_time, fill=reintervention, color=reintervention)) +
  geom_density(alpha=0.1) +
  ggtitle('Surgical Time') +
  xlim(c(0, 1000 ))+
  facet_grid(reintervention~.)


time_evolution[, .(surgical_time, reintervention)] %>% 
  .[, reintervention := as.numeric(as.character(reintervention))] %>% 
  .[ reintervention <= 3] %>% 
  lm(surgical_time~reintervention, data= .) %>% 
  summary %>% 
  coefficients %>% 
  print

time_evolution %>% 
  ggplot(aes(reintervention, surgical_time)) +
  geom_boxplot() +
  ggtitle('Surgical Time')
```

Note: linear model only up to 3 reinterventions (included)






