---
title: "Reinterventions exploration"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_knit$set(
  echo = FALSE, 
  warning = FALSE,
  root.dir=normalizePath('../../')
)
```

```{r warning=FALSE, include=FALSE}
library(readxl)
library(magrittr)
library(data.table)
library(stringr)
library(yaml)
library(zeallot)
library(DT)

source('code/basic.R')
source('code/utils.R')
source('code/reintervention/reinterventions-util.R')

c(time_evolution, complications, category_los, clinical_data) %<-% get_data()
controlling_vars <- read_yaml('code/reintervention/controling_vars.yml')
```

# Controling Variables

```{r comment=''}
cat(controlling_vars %>% as.yaml())
```

# Proportion of reinterventions by year

```{r comment='', echo=FALSE}
time_evolution %>% 
  .[reintervention != '0'] %>% 
  .[, .N, .(year=floor(diff_years) + 1)] %>% 
  .[, prop := round(N/sum(N), 3)*100] %>% 
  setorder(year) %>% 
  print
```


# Reinterventions Impact 


```{r echo=FALSE, include=FALSE}
lapply(1:6, function(y_){
  odi <- "{y_}Y. ODI - Score (%)" %>% f
  odi_base <- odi %>% get_base_outcome(first_visit=TRUE)
  srss <- "{y_}Y. SRS22 - SRS Subtotal score" %>% f
  srss_base <- srss %>% get_base_outcome(first_visit=TRUE)
  mcs <- "{y_}Y. SF36 - MCS" %>% f
  mcs_base <- mcs %>% get_base_outcome(first_visit=TRUE)
  pcs <- "{y_}Y. SF36 - PCS" %>% f
  pcs_base <- pcs %>% get_base_outcome(first_visit=TRUE)

  clinical_data %>%
    .[, .SD, .SDcols=c(controlling_vars, 'Code of the patient')] ->
    patient_quality

  clinical_data[, .(
    odi=get(odi) - get(odi_base),
    srss=get(srss) - get(srss_base),
    mcs=get(mcs) - get(mcs_base),
    pcs=get(pcs) - get(pcs_base),
    `Code of the patient`)] %>%
    merge(patient_quality, by='Code of the patient') %>%
    setnames('Code of the patient', 'patient_id')->
    patient_quality

  time_evolution %>%
    .[diff_years < y_, ] %>%
    .[, reintervention:=as.numeric(as.character(reintervention))] %>%
    .[, .(
      had_reintervention = max(reintervention) > 0,
      years_last_op = y_ - max(diff_years),
      reint_n = max(reintervention),
      blood_loss = max(blood_loss),
      surgical_time = max(surgical_time),
      hospitalization_time = max(hospitalization_time)
      ), .(patient_id, prior_group)] %>%
    merge(patient_quality, by='patient_id') %>%
    .[, outcome_year:=y_] ->
    res


  return(res)
}) %>%
  do.call(rbind, .) ->
  res

```


```{r echo=FALSE, warning=FALSE, message=FALSE}
res %>% 
  ggplot(aes(reint_n, odi, color=factor(outcome_year))) +
  geom_point(aes()) +
  geom_smooth(method='lm', se = FALSE) +
  ggtitle('ODI Score increment') ->
  data_plot
print(data_plot)


impact_var <- 'reint_n'
outcome <- 'odi'
controlling_vars_ <- controlling_vars

mean_outcome <- res[, .(mean_outcome=mean(get(outcome), na.rm = TRUE)),.(outcome_year)]

estimate_impacts(res, outcome, impact_var, controlling_vars_) %>% 
  data.table %>% 
  merge(mean_outcome, by='outcome_year') %>% 
  .[, relative_impact := round(Estimate/mean_outcome, 3)] %>% 
  .[, mean_outcome := round(mean_outcome, 3)] %>% 
  datatable
```

Dilution effect of `r outcome`: time since last operation (controlling by same variables plus number of reinterventions and outcome year) in first 6 years.

```{r echo=FALSE, warning=FALSE, message=FALSE}
estimate_dilution(res, outcome, controlling_vars_, sel_years=1:5) %>% 
  datatable
```


```{r echo=FALSE, warning=FALSE, message=FALSE}
res %>% 
  ggplot(aes(reint_n, srss, color=factor(outcome_year))) +
  geom_point(aes()) +
  geom_smooth(method='lm', se = FALSE) +
  ggtitle('SRSS Score increment')->
  data_plot
print(data_plot)

impact_var <- 'reint_n'
outcome <- 'srss'
controlling_vars_ <- controlling_vars

mean_outcome <- res[, .(mean_outcome=mean(get(outcome), na.rm = TRUE)),.(outcome_year)]

estimate_impacts(res, outcome, impact_var, controlling_vars_) %>% 
  data.table %>% 
  merge(mean_outcome, by='outcome_year') %>% 
  .[, relative_impact := round(Estimate/mean_outcome, 3)] %>% 
  .[, mean_outcome := round(mean_outcome, 3)] %>% 
  datatable
```

Dilution effect of `r outcome`: time since last operation (controlling by same variables plus number of reinterventions and outcome year) in first 5 years.

```{r echo=FALSE, warning=FALSE, message=FALSE}
estimate_dilution(res, outcome, controlling_vars_, sel_years=1:5) %>% 
  datatable
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
res %>% 
  ggplot(aes(reint_n, pcs, color=factor(outcome_year))) +
  geom_point(aes()) +
  geom_smooth(method='lm', se = FALSE) +
  ggtitle('PCS Score increment')->
  data_plot
print(data_plot)

impact_var <- 'reint_n'
outcome <- 'pcs'
controlling_vars_ <- controlling_vars

mean_outcome <- res[, .(mean_outcome=mean(get(outcome), na.rm = TRUE)),.(outcome_year)]

estimate_impacts(res, outcome, impact_var, controlling_vars_) %>% 
  data.table %>% 
  merge(mean_outcome, by='outcome_year') %>% 
  .[, relative_impact := round(Estimate/mean_outcome, 3)] %>% 
  .[, mean_outcome := round(mean_outcome, 3)] %>% 
  datatable
```

Dilution effect of `r outcome`: time since last operation (controlling by same variables plus number of reinterventions and outcome year) in first 6 years.

```{r echo=FALSE, warning=FALSE, message=FALSE}
estimate_dilution(res, outcome, controlling_vars_, sel_years=1:5) %>% 
  datatable
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
res %>% 
  ggplot(aes(reint_n, mcs, color=factor(outcome_year))) +
  geom_point(aes()) +
  geom_smooth(method='lm', se = FALSE) +
  ggtitle('MCS Score increment')->
  data_plot
print(data_plot)

impact_var <- 'reint_n'
outcome <- 'mcs'
controlling_vars_ <- controlling_vars

mean_outcome <- res[, .(mean_outcome=mean(odi, na.rm = TRUE)),.(outcome_year)]

estimate_impacts(res, outcome, impact_var, controlling_vars_) %>% 
  data.table %>% 
  merge(mean_outcome, by='outcome_year') %>% 
  .[, relative_impact := round(Estimate/mean_outcome, 3)] %>% 
  .[, mean_outcome := round(mean_outcome, 3)] %>% 
  datatable
```

Dilution effect of `r outcome`: time since last operation (controlling by same variables plus number of reinterventions and outcome year) in first  years.

```{r echo=FALSE, warning=FALSE, message=FALSE}
estimate_dilution(res, outcome, controlling_vars_, sel_years=1:5) %>% 
  datatable
```

<!-- # Impact by prior surgery groups -->

<!-- ```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""} -->

<!-- impact_var <- 'reint_n' -->
<!-- outcome <- 'odi' -->
<!-- controlling_vars_ <- controlling_vars -->

<!-- prior_groups <- res[, prior_group %>% unique] %>% sort -->
<!-- htmltools::h4(outcome) -->
<!-- for( prior_group_name in prior_groups){ -->
<!--   print(prior_group_name) -->
<!--   cat('\n') -->
<!--   res %>%  -->
<!--     .[prior_group==prior_group_name] %>%  -->
<!--     .[, prior_group := NULL] -> -->
<!--     res_group -->

<!--   res_group %>%  -->
<!--     estimate_impacts(outcome, impact_var, controlling_vars_, sel_years=1:3)  %>% print -->
<!-- } -->
<!-- ``` -->

<!-- ```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""} -->

<!-- impact_var <- 'reint_n' -->
<!-- outcome <- 'srss' -->
<!-- controlling_vars_ <- controlling_vars -->

<!-- prior_groups <- res[, prior_group %>% unique] %>% sort -->
<!-- htmltools::h4(outcome) -->
<!-- for( prior_group_name in prior_groups){ -->
<!--   print(prior_group_name) -->
<!--   cat('\n') -->
<!--   res %>%  -->
<!--     .[prior_group==prior_group_name] %>%  -->
<!--     .[, prior_group := NULL] -> -->
<!--     res_group -->

<!--   res_group %>%  -->
<!--     estimate_impacts(outcome, impact_var, controlling_vars_, sel_years=1:3)  %>% print -->
<!-- } -->
<!-- ``` -->

<!-- ```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""} -->

<!-- impact_var <- 'reint_n' -->
<!-- outcome <- 'pcs' -->
<!-- controlling_vars_ <- controlling_vars -->

<!-- prior_groups <- res[, prior_group %>% unique] %>% sort -->
<!-- htmltools::h4(outcome) -->
<!-- for( prior_group_name in prior_groups){ -->
<!--   print(prior_group_name) -->
<!--   cat('\n') -->
<!--   res %>%  -->
<!--     .[prior_group==prior_group_name] %>%  -->
<!--     .[, prior_group := NULL] -> -->
<!--     res_group -->

<!--   res_group %>%  -->
<!--     estimate_impacts(outcome, impact_var, controlling_vars_, sel_years=1:3)  %>% print -->
<!-- } -->
<!-- ``` -->


<!-- ```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""} -->

<!-- impact_var <- 'reint_n' -->
<!-- outcome <- 'mcs' -->
<!-- controlling_vars_ <- controlling_vars -->

<!-- prior_groups <- res[, prior_group %>% unique] %>% sort -->
<!-- htmltools::h4(outcome) -->
<!-- for( prior_group_name in prior_groups){ -->
<!--   print(prior_group_name) -->
<!--   cat('\n') -->
<!--   res %>%  -->
<!--     .[prior_group==prior_group_name] %>%  -->
<!--     .[, prior_group := NULL] -> -->
<!--     res_group -->

<!--   res_group %>%  -->
<!--     estimate_impacts(outcome, impact_var, controlling_vars_, sel_years=1:3)  %>% print -->
<!-- } -->
<!-- ``` -->

<!-- # Time Last Operation Impact  -->

<!-- ```{r echo=FALSE, warning=FALSE, message=FALSE} -->
<!-- res %>%  -->
<!--   ggplot(aes(years_last_op, odi, color=factor(outcome_year))) + -->
<!--   geom_point(aes()) + -->
<!--   geom_smooth(method='lm', se = FALSE) + -->
<!--   ggtitle('ODI Score increment') -> -->
<!--   data_plot -->
<!-- print(data_plot) -->

<!-- impact_var <- 'years_last_op' -->
<!-- outcome <- 'odi' -->
<!-- controlling_vars_ <- c(controlling_vars, 'reint_n') -->

<!-- estimate_impacts(res, outcome, impact_var, controlling_vars_) %>%  -->
<!--   datatable -->
<!-- ``` -->

<!-- ```{r echo=FALSE, warning=FALSE, message=FALSE} -->
<!-- res %>%  -->
<!--   ggplot(aes(years_last_op, srss, color=factor(outcome_year))) + -->
<!--   geom_point(aes()) + -->
<!--   geom_smooth(method='lm', se = FALSE) + -->
<!--   ggtitle('SRSS Score increment') -> -->
<!--   data_plot -->
<!-- print(data_plot) -->

<!-- impact_var <- 'years_last_op' -->
<!-- outcome <- 'srss' -->
<!-- controlling_vars_ <- c(controlling_vars, 'reint_n') -->

<!-- estimate_impacts(res, outcome, impact_var, controlling_vars_) %>%  -->
<!--   datatable -->
<!-- ``` -->

<!-- ```{r echo=FALSE, warning=FALSE, message=FALSE} -->
<!-- res %>%  -->
<!--   ggplot(aes(years_last_op, pcs, color=factor(outcome_year))) + -->
<!--   geom_point(aes()) + -->
<!--   geom_smooth(method='lm', se = FALSE) + -->
<!--   ggtitle('PCS Score increment') -> -->
<!--   data_plot -->
<!-- print(data_plot) -->

<!-- impact_var <- 'years_last_op' -->
<!-- outcome <- 'pcs' -->
<!-- controlling_vars_ <- c(controlling_vars, 'reint_n') -->

<!-- estimate_impacts(res, outcome, impact_var, controlling_vars_) %>%  -->
<!--   datatable -->
<!-- ``` -->

<!-- ```{r echo=FALSE, warning=FALSE, message=FALSE} -->
<!-- res %>%  -->
<!--   ggplot(aes(years_last_op, mcs, color=factor(outcome_year))) + -->
<!--   geom_point(aes()) + -->
<!--   geom_smooth(method='lm', se = FALSE) + -->
<!--   ggtitle('MCS Score increment') -> -->
<!--   data_plot -->
<!-- print(data_plot) -->

<!-- impact_var <- 'years_last_op' -->
<!-- outcome <- 'mcs' -->
<!-- controlling_vars_ <- c(controlling_vars, 'reint_n') -->

<!-- estimate_impacts(res, outcome, impact_var, controlling_vars_) %>%  -->
<!--   datatable -->
<!-- ``` -->

<!-- # Hospitalizaion Time Impact  -->

<!-- ```{r echo=FALSE, warning=FALSE, message=FALSE} -->
<!-- res %>%  -->
<!--   ggplot(aes(hospitalization_time, odi, color=factor(outcome_year))) + -->
<!--   geom_point(aes()) + -->
<!--   geom_smooth(method='lm', se = FALSE) + -->
<!--   ggtitle('ODI Score increment') -> -->
<!--   data_plot -->
<!-- print(data_plot) -->

<!-- impact_var <- 'hospitalization_time' -->
<!-- outcome <- 'odi' -->
<!-- controlling_vars_ <- c(controlling_vars, 'reint_n') -->

<!-- estimate_impacts(res, outcome, impact_var, controlling_vars_) %>%  -->
<!--   datatable -->
<!-- ``` -->

<!-- ```{r echo=FALSE, warning=FALSE, message=FALSE} -->
<!-- res %>%  -->
<!--   ggplot(aes(hospitalization_time, srss, color=factor(outcome_year))) + -->
<!--   geom_point(aes()) + -->
<!--   geom_smooth(method='lm', se = FALSE) + -->
<!--   ggtitle('SRSS Score increment') -> -->
<!--   data_plot -->
<!-- print(data_plot) -->

<!-- impact_var <- 'hospitalization_time' -->
<!-- outcome <- 'srss' -->
<!-- controlling_vars_ <- c(controlling_vars, 'reint_n') -->

<!-- estimate_impacts(res, outcome, impact_var, controlling_vars_) %>%  -->
<!--   datatable -->
<!-- ``` -->

<!-- ```{r echo=FALSE, warning=FALSE, message=FALSE} -->
<!-- res %>%  -->
<!--   ggplot(aes(hospitalization_time, pcs, color=factor(outcome_year))) + -->
<!--   geom_point(aes()) + -->
<!--   geom_smooth(method='lm', se = FALSE) + -->
<!--   ggtitle('PCS Score increment') -> -->
<!--   data_plot -->
<!-- print(data_plot) -->

<!-- impact_var <- 'hospitalization_time' -->
<!-- outcome <- 'pcs' -->
<!-- controlling_vars_ <- c(controlling_vars, 'reint_n') -->

<!-- estimate_impacts(res, outcome, impact_var, controlling_vars_) %>%  -->
<!--   datatable -->
<!-- ``` -->

<!-- ```{r echo=FALSE, warning=FALSE, message=FALSE} -->
<!-- res %>%  -->
<!--   ggplot(aes(hospitalization_time, mcs, color=factor(outcome_year))) + -->
<!--   geom_point(aes()) + -->
<!--   geom_smooth(method='lm', se = FALSE) + -->
<!--   ggtitle('MCS Score increment') -> -->
<!--   data_plot -->
<!-- print(data_plot) -->

<!-- impact_var <- 'hospitalization_time' -->
<!-- outcome <- 'mcs' -->
<!-- controlling_vars_ <- c(controlling_vars, 'reint_n') -->

<!-- estimate_impacts(res, outcome, impact_var, controlling_vars_) %>%  -->
<!--   datatable -->
<!-- ``` -->

<!-- # Blood Loss Impact  -->

<!-- ```{r echo=FALSE, warning=FALSE, message=FALSE} -->
<!-- res %>%  -->
<!--   ggplot(aes(blood_loss, odi, color=factor(outcome_year))) + -->
<!--   geom_point(aes()) + -->
<!--   geom_smooth(method='lm', se = FALSE) + -->
<!--   ggtitle('ODI Score increment') -> -->
<!--   data_plot -->
<!-- print(data_plot) -->

<!-- impact_var <- 'blood_loss' -->
<!-- outcome <- 'odi' -->
<!-- controlling_vars_ <- c(controlling_vars, 'reint_n') -->

<!-- estimate_impacts(res, outcome, impact_var, controlling_vars_) %>%  -->
<!--   datatable -->
<!-- ``` -->

<!-- ```{r echo=FALSE, warning=FALSE, message=FALSE} -->
<!-- res %>%  -->
<!--   ggplot(aes(blood_loss, srss, color=factor(outcome_year))) + -->
<!--   geom_point(aes()) + -->
<!--   geom_smooth(method='lm', se = FALSE) + -->
<!--   ggtitle('SRSS Score increment') -> -->
<!--   data_plot -->
<!-- print(data_plot) -->

<!-- impact_var <- 'blood_loss' -->
<!-- outcome <- 'srss' -->
<!-- controlling_vars_ <- c(controlling_vars, 'reint_n') -->

<!-- estimate_impacts(res, outcome, impact_var, controlling_vars_) %>%  -->
<!--   datatable -->
<!-- ``` -->

<!-- ```{r echo=FALSE, warning=FALSE, message=FALSE} -->
<!-- res %>%  -->
<!--   ggplot(aes(blood_loss, pcs, color=factor(outcome_year))) + -->
<!--   geom_point(aes()) + -->
<!--   geom_smooth(method='lm', se = FALSE) + -->
<!--   ggtitle('PCS Score increment') -> -->
<!--   data_plot -->
<!-- print(data_plot) -->

<!-- impact_var <- 'blood_loss' -->
<!-- outcome <- 'pcs' -->
<!-- controlling_vars_ <- c(controlling_vars, 'reint_n') -->

<!-- estimate_impacts(res, outcome, impact_var, controlling_vars_) %>%  -->
<!--   datatable -->
<!-- ``` -->

<!-- ```{r echo=FALSE, warning=FALSE, message=FALSE} -->
<!-- res %>%  -->
<!--   ggplot(aes(blood_loss, mcs, color=factor(outcome_year))) + -->
<!--   geom_point(aes()) + -->
<!--   geom_smooth(method='lm', se = FALSE) + -->
<!--   ggtitle('MCS Score increment') -> -->
<!--   data_plot -->
<!-- print(data_plot) -->

<!-- impact_var <- 'blood_loss' -->
<!-- outcome <- 'mcs' -->
<!-- controlling_vars_ <- c(controlling_vars, 'reint_n') -->

<!-- estimate_impacts(res, outcome, impact_var, controlling_vars_) %>%  -->
<!--   datatable -->
<!-- ``` -->

<!-- # Surgical Time Impact  -->

<!-- ```{r echo=FALSE, warning=FALSE, message=FALSE} -->
<!-- res %>%  -->
<!--   ggplot(aes(surgical_time, odi, color=factor(outcome_year))) + -->
<!--   geom_point(aes()) + -->
<!--   geom_smooth(method='lm', se = FALSE) + -->
<!--   ggtitle('ODI Score increment') -> -->
<!--   data_plot -->
<!-- print(data_plot) -->

<!-- impact_var <- 'surgical_time' -->
<!-- outcome <- 'odi' -->
<!-- controlling_vars_ <- c(controlling_vars, 'reint_n') -->

<!-- estimate_impacts(res, outcome, impact_var, controlling_vars_) %>%  -->
<!--   datatable -->
<!-- ``` -->

<!-- ```{r echo=FALSE, warning=FALSE, message=FALSE} -->
<!-- res %>%  -->
<!--   ggplot(aes(surgical_time, srss, color=factor(outcome_year))) + -->
<!--   geom_point(aes()) + -->
<!--   geom_smooth(method='lm', se = FALSE) + -->
<!--   ggtitle('SRSS Score increment') -> -->
<!--   data_plot -->
<!-- print(data_plot) -->

<!-- impact_var <- 'surgical_time' -->
<!-- outcome <- 'srss' -->
<!-- controlling_vars_ <- c(controlling_vars, 'reint_n') -->

<!-- estimate_impacts(res, outcome, impact_var, controlling_vars_) %>%  -->
<!--   datatable -->
<!-- ``` -->

<!-- ```{r echo=FALSE, warning=FALSE, message=FALSE} -->
<!-- res %>%  -->
<!--   ggplot(aes(surgical_time, pcs, color=factor(outcome_year))) + -->
<!--   geom_point(aes()) + -->
<!--   geom_smooth(method='lm', se = FALSE) + -->
<!--   ggtitle('PCS Score increment') -> -->
<!--   data_plot -->
<!-- print(data_plot) -->

<!-- impact_var <- 'surgical_time' -->
<!-- outcome <- 'pcs' -->
<!-- controlling_vars_ <- c(controlling_vars, 'reint_n') -->

<!-- estimate_impacts(res, outcome, impact_var, controlling_vars_) %>%  -->
<!--   datatable -->
<!-- ``` -->

<!-- ```{r echo=FALSE, warning=FALSE, message=FALSE} -->
<!-- res %>%  -->
<!--   ggplot(aes(surgical_time, mcs, color=factor(outcome_year))) + -->
<!--   geom_point(aes()) + -->
<!--   geom_smooth(method='lm', se = FALSE) + -->
<!--   ggtitle('MCS Score increment') -> -->
<!--   data_plot -->
<!-- print(data_plot) -->

<!-- impact_var <- 'surgical_time' -->
<!-- outcome <- 'mcs' -->
<!-- controlling_vars_ <- c(controlling_vars, 'reint_n') -->

<!-- estimate_impacts(res, outcome, impact_var, controlling_vars_) %>%  -->
<!--   datatable -->
<!-- ``` -->



<!-- # Quality life increment for reinterventions -->

<!-- ```{r echo=FALSE, include=FALSE} -->
<!-- lapply(1:6, function(y_){ -->
<!--   odi <- "{y_}Y. ODI - Score (%)" %>% f -->
<!--   odi_base <- odi %>% get_base_outcome(first_visit=TRUE) -->
<!--   srss <- "{y_}Y. SRS22 - SRS Subtotal score" %>% f -->
<!--   srss_base <- srss %>% get_base_outcome(first_visit=TRUE) -->
<!--   mcs <- "{y_}Y. SF36 - MCS" %>% f -->
<!--   mcs_base <- mcs %>% get_base_outcome(first_visit=TRUE) -->
<!--   pcs <- "{y_}Y. SF36 - PCS" %>% f -->
<!--   pcs_base <- pcs %>% get_base_outcome(first_visit=TRUE) -->

<!--   clinical_data[, .( -->
<!--     odi=get(odi) - get(odi_base),  -->
<!--     srss=get(srss) - get(srss_base),  -->
<!--     mcs=get(mcs) - get(mcs_base),  -->
<!--     pcs=get(pcs) - get(pcs_base), -->
<!--     patient_id=`Code of the patient`)] -> -->
<!--     patient_quality -->

<!--   time_evolution %>%  -->
<!--     .[diff_years < y_, ] %>%  -->
<!--     .[, .(last_operation= max(diff_years)), .(patient_id)] %>%  -->
<!--     .[, last_operation := as.numeric(last_operation)] %>%  -->
<!--     merge(patient_quality, by='patient_id') %>%  -->
<!--     .[, outcome_year:=y_] -> -->
<!--     res -->

<!--   get_lm_info <- function(data_, name){ -->
<!--     "{name}~last_operation" %>% f %>% as.formula() %>%  -->
<!--     lm(data=data_) %>% summary %>% .$coefficients %>%  -->
<!--       .[2, c(1, 2)] %>% round(1) -> lm_info -->

<!--     "{lm_info[1]}\n({lm_info[2]})" %>% f -->
<!--   } -->

<!--   res %>%  -->
<!--     .[, odi_info:=get_lm_info(.SD, 'odi')] %>%  -->
<!--     .[, srss_info:=get_lm_info(.SD, 'srss')] %>%  -->
<!--     .[, mcs_info:=get_lm_info(.SD, 'mcs')] %>%  -->
<!--     .[, pcs_info:=get_lm_info(.SD, 'pcs')] -->

<!--   return(res) -->
<!-- }) %>%  -->
<!--   do.call(rbind, .) ->  -->
<!--   res -->
<!-- ``` -->


<!-- ```{r echo=FALSE, warning=FALSE} -->
<!-- info.labs <- res[, .(info=unique(odi_info)), .(outcome_year)] -->
<!-- outcome_year.labs <- info.labs[, info] -->
<!-- names(outcome_year.labs) <- info.labs[, outcome_year] -->

<!-- res %>%  -->
<!--   ggplot(aes(last_operation, odi)) + -->
<!--   geom_point() + -->
<!--   geom_jitter(width=0.005) + -->
<!--   ggtitle('ODI Score increment') + -->
<!--   geom_smooth(method='lm') + -->
<!--   facet_grid(outcome_year~.,  -->
<!--     labeller=labeller(outcome_year=outcome_year.labs)) -->
<!-- ``` -->


<!-- ```{r echo=FALSE, warning=FALSE} -->
<!-- info.labs <- res[, .(info=unique(srss_info)), .(outcome_year)] -->
<!-- outcome_year.labs <- info.labs[, info] -->
<!-- names(outcome_year.labs) <- info.labs[, outcome_year] -->

<!-- res %>%  -->
<!--   ggplot(aes(last_operation, srss)) + -->
<!--   geom_point() + -->
<!--   geom_jitter(width=0.005) + -->
<!--   geom_smooth(method='lm') + -->
<!--   ggtitle('SRS22 Subtotal increment') + -->
<!--   facet_grid(outcome_year~.,  -->
<!--     labeller=labeller(outcome_year=outcome_year.labs)) -->
<!-- ``` -->


<!-- ```{r echo=FALSE, warning=FALSE} -->
<!-- info.labs <- res[, .(info=unique(mcs_info)), .(outcome_year)] -->
<!-- outcome_year.labs <- info.labs[, info] -->
<!-- names(outcome_year.labs) <- info.labs[, outcome_year] -->

<!-- res %>%  -->
<!--   ggplot(aes(last_operation, mcs)) + -->
<!--   geom_point() + -->
<!--   geom_jitter(width=0.005) + -->
<!--   geom_smooth(method='lm') + -->
<!--   ggtitle('SF36 - MCS increment') + -->
<!--   facet_grid(outcome_year~.,  -->
<!--     labeller=labeller(outcome_year=outcome_year.labs)) -->
<!-- ``` -->

<!-- ```{r echo=FALSE, warning=FALSE} -->
<!-- info.labs <- res[, .(info=unique(pcs_info)), .(outcome_year)] -->
<!-- outcome_year.labs <- info.labs[, info] -->
<!-- names(outcome_year.labs) <- info.labs[, outcome_year] -->

<!-- res %>%  -->
<!--   ggplot(aes(last_operation, pcs)) + -->
<!--   geom_point() + -->
<!--   geom_jitter(width=0.005) + -->
<!--   geom_smooth(method='lm') + -->
<!--   ggtitle('SF36 - MCS increment') + -->
<!--   facet_grid(outcome_year~.,  -->
<!--     labeller=labeller(outcome_year=outcome_year.labs)) -->
<!-- ``` -->

<!-- ### Had Intervention -->

<!-- For each outcome year, whether the pacient had an intervention before the questionaire -->
<!-- ```{r echo=FALSE, warning=FALSE} -->
<!-- res %>%  -->
<!--   ggplot(aes(last_operation, pcs)) + -->
<!--   geom_point() + -->
<!--   geom_jitter(width=0.005) + -->
<!--   geom_smooth(method='lm') + -->
<!--   ggtitle('SF36 - PCS increment') + -->
<!--   facet_grid(outcome_year~.) -->
<!-- ``` -->

<!-- ```{r echo=FALSE, warning=FALSE} -->
<!-- lapply(1:6, function(y_){ -->
<!--   odi <- "{y_}Y. ODI - Score (%)" %>% f -->
<!--   odi_base <- odi %>% get_base_outcome(first_visit=TRUE) -->
<!--   srss <- "{y_}Y. SRS22 - SRS Subtotal score" %>% f -->
<!--   srss_base <- srss %>% get_base_outcome(first_visit=TRUE) -->
<!--   mcs <- "{y_}Y. SF36 - MCS" %>% f -->
<!--   mcs_base <- mcs %>% get_base_outcome(first_visit=TRUE) -->
<!--   pcs <- "{y_}Y. SF36 - PCS" %>% f -->
<!--   pcs_base <- pcs %>% get_base_outcome(first_visit=TRUE) -->

<!--   clinical_data[, .( -->
<!--     odi=get(odi) - get(odi_base),  -->
<!--     srss=get(srss) - get(srss_base),  -->
<!--     mcs=get(mcs) - get(mcs_base),  -->
<!--     pcs=get(pcs) - get(pcs_base), -->
<!--     patient_id=`Code of the patient`)] -> -->
<!--     patient_quality -->

<!--   time_evolution %>%  -->
<!--     .[diff_years < y_, ] %>%  -->
<!--     .[, reint_num:=as.numeric(as.character(reintervention))] %>%  -->
<!--     .[, had_reintervention := max(reint_num) > 0, patient_id] %>%  -->
<!--     merge(patient_quality, by='patient_id') %>%  -->
<!--     .[, outcome_year:=factor(y_)] -> -->
<!--     res -->

<!--   return(res) -->
<!-- }) %>%  -->
<!--   do.call(rbind, .) ->  -->
<!--   res -->
<!-- ``` -->


<!-- ```{r echo=FALSE} -->
<!-- res %>%  -->
<!--   ggplot(aes(outcome_year, odi, fill=had_reintervention)) + -->
<!--   geom_boxplot(position = "dodge2") + -->
<!--   ggtitle('ODI Score increment') -->
<!-- ``` -->


<!-- ```{r echo=FALSE} -->
<!-- res %>%  -->
<!--   ggplot(aes(outcome_year, srss, fill=had_reintervention)) + -->
<!--   geom_boxplot(position = "dodge2") + -->
<!--   ggtitle('SRS22 Subtotal increment') -->
<!-- ``` -->


<!-- ```{r echo=FALSE} -->
<!-- res %>%  -->
<!--   ggplot(aes(outcome_year, mcs, fill=had_reintervention)) + -->
<!--   geom_boxplot(position = "dodge2") + -->
<!--   ggtitle('SF36 - MCS increment') -->
<!-- ``` -->


<!-- ```{r echo=FALSE} -->
<!-- res %>%  -->
<!--   ggplot(aes(outcome_year, pcs, fill=had_reintervention)) + -->
<!--   geom_boxplot(position = "dodge2") + -->
<!--   ggtitle('SF36 - PCS increment')  -->
<!-- ``` -->


<!-- # Had intervention evolution -->

<!-- ```{r echo=FALSE} -->
<!-- lapply(1:6, function(y_){ -->
<!--   odi <- "{y_}Y. ODI - Score (%)" %>% f -->
<!--   odi_base <- odi %>% get_base_outcome(first_visit=TRUE) -->
<!--   srss <- "{y_}Y. SRS22 - SRS Subtotal score" %>% f -->
<!--   srss_base <- srss %>% get_base_outcome(first_visit=TRUE) -->
<!--   mcs <- "{y_}Y. SF36 - MCS" %>% f -->
<!--   mcs_base <- mcs %>% get_base_outcome(first_visit=TRUE) -->
<!--   pcs <- "{y_}Y. SF36 - PCS" %>% f -->
<!--   pcs_base <- pcs %>% get_base_outcome(first_visit=TRUE) -->

<!--   clinical_data[, .( -->
<!--     odi=get(odi) - get(odi_base),  -->
<!--     srss=get(srss) - get(srss_base),  -->
<!--     mcs=get(mcs) - get(mcs_base),  -->
<!--     pcs=get(pcs) - get(pcs_base), -->
<!--     patient_id=`Code of the patient`)] -> -->
<!--     patient_quality -->

<!--   time_evolution %>%  -->
<!--     .[diff_years < y_, ] %>%  -->
<!--     .[, sel_year:=y_] %>%  -->
<!--     .[, reint_num:=as.numeric(as.character(reintervention))] %>%  -->
<!--     .[, had_reintervention := max(reint_num) > 0, patient_id] %>%  -->
<!--     merge(patient_quality, by='patient_id') %>%  -->
<!--     .[, outcome_year:=factor(y_)] -> -->
<!--     res -->

<!--   return(res) -->
<!-- }) %>%  -->
<!--   do.call(rbind, .) ->  -->
<!--   res -->
<!-- ``` -->

<!-- Black lines are the mean value of the score -->

<!-- ```{r echo=FALSE} -->
<!-- mean_val <- res[, mean(odi %>% na.omit)] -->
<!-- ggplot(res, aes(sel_year, odi, color=had_reintervention)) + -->
<!--   geom_point() + -->
<!--   geom_smooth(method='lm') + -->
<!--   geom_abline(slope=0, intercept = mean_val, color='black') + -->
<!--   ggtitle('ODI Score increment') -->
<!-- ``` -->


<!-- ```{r echo=FALSE} -->
<!-- mean_val <- res[, mean(srss %>% na.omit)] -->
<!-- ggplot(res, aes(sel_year, srss, color=had_reintervention)) + -->
<!--   geom_point() + -->
<!--   geom_smooth(method='lm') + -->
<!--   geom_abline(slope=0, intercept = mean_val, color='black') + -->
<!--   ggtitle('SRS22 Subtotal increment') -->
<!-- ``` -->

<!-- ```{r echo=FALSE} -->
<!-- mean_val <- res[, mean(mcs %>% na.omit)] -->
<!-- ggplot(res, aes(sel_year, mcs, color=had_reintervention)) + -->
<!--   geom_point() + -->
<!--   geom_smooth(method='lm') + -->
<!--   geom_abline(slope=0, intercept = mean_val, color='black') + -->
<!--   ggtitle('SF36 - MCS increment') -->
<!-- ``` -->

<!-- ```{r echo=FALSE} -->
<!-- mean_val <- res[, mean(pcs %>% na.omit)] -->
<!-- ggplot(res, aes(sel_year, pcs, color=had_reintervention)) + -->
<!--   geom_point() + -->
<!--   geom_smooth(method='lm') + -->
<!--   geom_abline(slope=0, intercept = mean_val, color='black') + -->
<!--   ggtitle('SF36 - PCS increment') -->
<!-- ``` -->


