---
title: "LIV Iliac/L5"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, include=FALSE, message=FALSE, warning=FALSE, comment="")
knitr::opts_knit$set(root.dir=normalizePath('../'))
```

```{r}
library(data.table)
library(magrittr)
library(yaml)

source('patient_selection.R')
```

```{r, message=FALSE}
analysis_vars <- read_yaml('descriptive.yml')
xls_path_ <- '../../data/ESSG extraction July 2021 DEF_v3.xlsx'
data_ <- get_data(xls_path=xls_path_)
```
Initial Patients: `r data_[, .N]`

```{r}
data_ %<>% 
  .[`Posterior Instrumented Fusion` == 'Yes'] %>% 
  .[`Number of Posterior Instrumented Levels` > 3]
```
With Posterior Instrumented Fusion & Number of Posterior Instrumented Levels > 3: `r data_[, .N]`




```{r include=TRUE}
data_[, `Posterior Instrumented Fusion: Upper / Lower Levels`] %>% 
  sapply(. %>% strsplit('-') %>% .[[1]] %>% .[2]) ->
  post_intr_fusion

data_[post_intr_fusion == 'Iliac', type := 'Iliac']
data_[post_intr_fusion == 'L5', type := 'L5']
data_[post_intr_fusion == 'L4', type := 'L4']
data_ %<>% .[!is.na(type)] 

data_[, .N, type]
```

<!-- With 5Y FU -->
<!-- ```{r include=TRUE} -->
<!-- data_ %<>% .[followup_5y==TRUE] -->
<!-- data_[, .N, type] -->
<!-- ``` -->

```{r include=FALSE}
write.csv(data_[, .(`Code of the patient`, type)], "liv_Iliac_l5_l4_review/patients_iliac_l5_l4.csv")
```



Patients who end up intrumented until pelvis
```{r include=TRUE, echo=TRUE}
revision <- read_excel(xls_path, sheet="Revision surgeries") %>% 
  as.data.table()

revision[, `Posterior Instrumented Fusion: Upper / Lower Levels`] %>% 
  sapply(. %>% strsplit('-') %>% .[[1]] %>% .[2]) ->
  post_intr_fusion

reint_iliac <- revision[post_intr_fusion=='Iliac', `Code of the patient`]

data_[`Code of the patient` %in% reint_iliac, `Code of the patient` %>% uniqueN, type]
```

UIV frequencies
```{r include=TRUE}
data_[, `Posterior Instrumented Fusion: Upper / Lower Levels`] %>% 
  sapply(. %>% strsplit('-') %>% .[[1]] %>% .[1]) -> 
  post_intr_fusion_upper 
data.table(uiv = post_intr_fusion_upper) %>% 
  .[, .N, uiv] %>% 
  setorder(uiv) %>% 
  print
```

```{r}
treatment_ <- 'type'
treatment_vals <- c('Iliac', 'L5', 'L4')
treatment_n <- len(treatment_vals)
```

```{r}
data_treats <- list()
for(treatment_pos in 1:treatment_n){
  data_treats[[treatment_pos]] <- data_[get(treatment_) == treatment_vals[treatment_pos]]
}
```

```{r include)TRUE}
data_[, .N, c("Non_instrumented_segments", treatment_)] %>% 
  setorder(type, Non_instrumented_segments) %>% na.omit %>% print
```


### P-valor ASA 1 Iliac vs L5 
```{r include=TRUE}
var_ <- "ASA classification"
data_[, .(
  treatment=get(treatment_), variable=get(var_))] ->
  data__

data__[, variable := ifelse(as.character(variable) == 1, 1, 2)]
res <- data__[, .(asa_1 = sum(variable == 1), .N), treatment] %>% 
  .[!is.na(treatment)]

print(res)
```


```{r include=TRUE}
n1 <- 1
n2 <- 2
print("P-values Treatment {treatment_vals[n1]} vs Treatment {treatment_vals[n2]}" %>% f)
prop.test(
  c(
    res[treatment==treatment_vals[n1]]$asa_1,
    res[treatment==treatment_vals[n2]]$asa_1
  ),
  c(
    res[treatment==treatment_vals[n1]]$N,
    res[treatment==treatment_vals[n2]]$N
  ))$p.val
```

```{r include=TRUE}
n1 <- 1
n2 <- 3
print("P-values Treatment {treatment_vals[n1]} vs Treatment {treatment_vals[n2]}" %>% f)
prop.test(
  c(
    res[treatment==treatment_vals[n1]]$asa_1,
    res[treatment==treatment_vals[n2]]$asa_1
  ),
  c(
    res[treatment==treatment_vals[n1]]$N,
    res[treatment==treatment_vals[n2]]$N
  ))$p.val
```

```{r include=TRUE}
n1 <- 2
n2 <- 3
print("P-values Treatment {treatment_vals[n1]} vs Treatment {treatment_vals[n2]}" %>% f)
prop.test(
  c(
    res[treatment==treatment_vals[n1]]$asa_1,
    res[treatment==treatment_vals[n2]]$asa_1
  ),
  c(
    res[treatment==treatment_vals[n1]]$N,
    res[treatment==treatment_vals[n2]]$N
  ))$p.val
```

### P-valor Prior Spine Surgery Yes Iliac vs L5
```{r include=TRUE}
var_ <- "Prior Spine Surgery"
data_[, .(
  treatment=get(treatment_), variable=get(var_))] ->
  data__

res <- data__[, .(prior_yes = sum(variable == 'Yes'), .N), treatment] %>% 
  .[!is.na(treatment)]

print(res)
```

  
```{r include=TRUE}
n1 <- 1
n2 <- 2
print("P-values Treatment {treatment_vals[n1]} vs Treatment {treatment_vals[n2]}" %>% f)
prop.test(
  c(
    res[treatment==treatment_vals[n1]]$prior_yes,
    res[treatment==treatment_vals[n2]]$prior_yes
  ),
  c(
    res[treatment==treatment_vals[n1]]$N,
    res[treatment==treatment_vals[n2]]$N
  ))$p.val
```

```{r include=TRUE}
n1 <- 1
n2 <- 3
print("P-values Treatment {treatment_vals[n1]} vs Treatment {treatment_vals[n2]}" %>% f)
prop.test(
  c(
    res[treatment==treatment_vals[n1]]$prior_yes,
    res[treatment==treatment_vals[n2]]$prior_yes
  ),
  c(
    res[treatment==treatment_vals[n1]]$N,
    res[treatment==treatment_vals[n2]]$N
  ))$p.val
```

```{r include=TRUE}
n1 <- 2
n2 <- 3
print("P-values Treatment {treatment_vals[n1]} vs Treatment {treatment_vals[n2]}" %>% f)
prop.test(
  c(
    res[treatment==treatment_vals[n1]]$prior_yes,
    res[treatment==treatment_vals[n2]]$prior_yes
  ),
  c(
    res[treatment==treatment_vals[n1]]$N,
    res[treatment==treatment_vals[n2]]$N
  ))$p.val
```


### 3CO

```{r include=TRUE}
var_ <- "3CO"
data_[, .(
  treatment=get(treatment_), variable=get(var_))] ->
  data__

res <- data__[, .(prior_yes = sum(variable == 'Yes'), .N), treatment] %>% 
  .[!is.na(treatment)]

print(res)
```

  
```{r include=TRUE}
n1 <- 1
n2 <- 2
print("P-values Treatment {treatment_vals[n1]} vs Treatment {treatment_vals[n2]}" %>% f)
prop.test(
  c(
    res[treatment==treatment_vals[n1]]$prior_yes,
    res[treatment==treatment_vals[n2]]$prior_yes
  ),
  c(
    res[treatment==treatment_vals[n1]]$N,
    res[treatment==treatment_vals[n2]]$N
  ))$p.val
```

```{r include=TRUE}
n1 <- 1
n2 <- 3
print("P-values Treatment {treatment_vals[n1]} vs Treatment {treatment_vals[n2]}" %>% f)
prop.test(
  c(
    res[treatment==treatment_vals[n1]]$prior_yes,
    res[treatment==treatment_vals[n2]]$prior_yes
  ),
  c(
    res[treatment==treatment_vals[n1]]$N,
    res[treatment==treatment_vals[n2]]$N
  ))$p.val
```

```{r include=TRUE}
n1 <- 2
n2 <- 3
print("P-values Treatment {treatment_vals[n1]} vs Treatment {treatment_vals[n2]}" %>% f)
prop.test(
  c(
    res[treatment==treatment_vals[n1]]$prior_yes,
    res[treatment==treatment_vals[n2]]$prior_yes
  ),
  c(
    res[treatment==treatment_vals[n1]]$N,
    res[treatment==treatment_vals[n2]]$N
  ))$p.val
```



### Demographics
```{r echo=FALSE, comment="", include=TRUE}
for(var_ in analysis_vars$demographics ){
  
  res <- stats_fun(data_[[var_]])
  res_treats <- list()
  for(treatment_pos in 1:treatment_n){
    res_treats[[treatment_pos]] <- stats_fun(
      data_treats[[treatment_pos]][[var_]])
  }
  
  for( res_name in names(res) ){
    cat(var_)
    cat(' - ')
    cat(res_name)
    cat('\n')
    
    cat('All\n')
    print(res[[res_name]])

    for(treatment_pos in 1:treatment_n){
      cat(treatment_vals[treatment_pos])
      cat('\n')
      print(res_treats[[treatment_pos]][[res_name]])
      cat('\n')
    }
    
    if( res_name == 'mean'){
      for(n1 in 1:(treatment_n-1)){
        for(n2 in (n1+1):treatment_n){
          p.val <- calc_p_vals(data_, var_, treatment_, treatment_vals[c(n1, n2)])
          if(!is.null(p.val)){
            cat('{treatment_vals[n1]} vs {treatment_vals[n2]} p-value:\n' %>% f)
            print(p.val)
            cat('\n\n')
          }
        }
      }
    }
  }
  cat('\n\n')
}
```


### Radiology
```{r echo=FALSE, comment="", include=TRUE}
for(var_ in analysis_vars$radiology ){
  var_6w <- "6W. {var_}" %>% f
  var_6m <- "6M. {var_}" %>% f
  var_1y <- "1Y. {var_}" %>% f
  var_2y <- "2Y. {var_}" %>% f
  var_5y <- "5Y. {var_}" %>% f
  vars_years <- c(var_, var_6w, var_6m, var_1y, var_2y, var_5y)
  for(var_y in vars_years){
    res <- stats_fun(data_[[var_y]])
    res_treats <- list()
    for(treatment_pos in 1:treatment_n){
      res_treats[[treatment_pos]] <- stats_fun(
        data_treats[[treatment_pos]][[var_y]])
    }
    for( res_name in names(res) ){
      cat(var_y)
      cat(' - ')
      cat(res_name)
      cat('\n')
      
      cat('All\n')
      print(res[[res_name]])
      
      for(treatment_pos in 1:treatment_n){
        cat(treatment_vals[treatment_pos])
        cat('\n')
        print(res_treats[[treatment_pos]][[res_name]])
        cat('\n')
      }
      
      if( res_name == 'mean'){
        for(n1 in 1:(treatment_n-1)){
          for(n2 in (n1+1):treatment_n){
            p.val <- calc_p_vals(data_, var_y, treatment_, treatment_vals[c(n1, n2)])
            if(!is.null(p.val)){
              cat('{treatment_vals[n1]} vs {treatment_vals[n2]} p-value:\n' %>% f)
              print(p.val)
              cat('\n\n')
            }
          }
        }
      }
    }
    cat('\n\n')
  }
    
  cat('{var_} tests all\n' %>% f)
  val_ <- data_[[var_]]
  val_6w <- data_[[var_6w]]
  val_2y <- data_[[var_2y]]
  val_5y <- data_[[var_5y]]
  cat('\nPreop vs 6w p-value\n')
  cat(t.test(val_6w , val_)$p.val)
  cat('\n\n')
  cat('Preop vs 2y p-value\n')
  cat(t.test(val_2y, val_)$p.val)
  cat('\n\n')
  cat('Preop vs 5y p-value\n')
  cat(t.test(val_5y, val_)$p.val)
  cat('\n\n')
  cat('6w vs 2y p-value\n')
  cat(t.test(val_2y, val_6w)$p.val)
  cat('\n\n')
  cat('2y vs 5y p-value\n')
  cat(t.test(val_5y, val_2y)$p.val)
  cat('\n\n')
  cat('6w vs 5y p-value\n')
  cat(t.test(val_5y, val_6w)$p.val)
  cat('\n\n')
  
  for(treatment_pos in 1:treatment_n){
    cat('{var_} tests {treatment_vals[treatment_pos]}\n' %>% f)
    val_ <- data_treats[[treatment_pos]][[var_]]
    val_6w <- data_treats[[treatment_pos]][[var_6w]]
    val_2y <- data_treats[[treatment_pos]][[var_2y]]
    val_5y <- data_treats[[treatment_pos]][[var_5y]]
    cat('\nPreop vs 6w p-value\n')
    cat(t.test(val_6w , val_)$p.val)
    cat('\n\n')
    cat('Preop vs 2y p-value\n')
    cat(t.test(val_2y, val_)$p.val)
    cat('\n\n')
    cat('Preop vs 5y p-value\n')
    cat(t.test(val_5y, val_)$p.val)
    cat('\n\n')
    cat('6w vs 2y p-value\n')
    cat(t.test(val_2y, val_6w)$p.val)
    cat('\n\n')
    cat('2y vs 5y p-value\n')
    cat(t.test(val_5y, val_2y)$p.val)
    cat('\n\n')
    cat('6w vs 5y p-value\n')
    cat(t.test(val_5y, val_6w)$p.val)
    cat('\n\n')
  }
}
```


### Quality of Life
```{r echo=FALSE, comment="", include=TRUE}
for(var_ in analysis_vars$quality ){
  var_6m <- "6M. {var_}" %>% f
  var_1y <- "1Y. {var_}" %>% f
  var_2y <- "2Y. {var_}" %>% f
  var_5y <- "5Y. {var_}" %>% f
  vars_years <- c(var_, var_6m, var_1y, var_2y, var_5y)
  for(var_y in vars_years){
    res <- stats_fun(data_[[var_y]])
    res_treats <- list()
    for(treatment_pos in 1:treatment_n){
      res_treats[[treatment_pos]] <- stats_fun(
        data_treats[[treatment_pos]][[var_y]])
    }
    for( res_name in names(res) ){
      cat(var_y)
      cat(' - ')
      cat(res_name)
      cat('\n')
      
      cat('All\n')
      print(res[[res_name]])
      
      for(treatment_pos in 1:treatment_n){
        cat(treatment_vals[treatment_pos])
        cat('\n')
        print(res_treats[[treatment_pos]][[res_name]])
        cat('\n')
      }
      
      if( res_name == 'mean'){
        for(n1 in 1:(treatment_n-1)){
          for(n2 in (n1+1):treatment_n){
            p.val <- calc_p_vals(data_, var_y, treatment_, treatment_vals[c(n1, n2)])
            if(!is.null(p.val)){
              cat('{treatment_vals[n1]} vs {treatment_vals[n2]} p-value:\n' %>% f)
              print(p.val)
              cat('\n\n')
            }
          }
        }
      }
    }
    cat('\n\n')
  }
  
  cat('{var_} tests all\n' %>% f)
  val_ <- data_[[var_]]
  val_6m <- data_[[var_6m]]
  val_2y <- data_[[var_2y]]
  val_5y <- data_[[var_5y]]
  cat('\nPreop vs 6m p-value\n')
  cat(t.test(val_6m , val_)$p.val)
  cat('\n\n')
  cat('Preop vs 2y p-value\n')
  cat(t.test(val_2y, val_)$p.val)
  cat('\n\n')
  cat('Preop vs 5y p-value\n')
  cat(t.test(val_5y, val_)$p.val)
  cat('\n\n')
  cat('6m vs 2y p-value\n')
  cat(t.test(val_2y, val_6m)$p.val)
  cat('\n\n')
  cat('2y vs 5y p-value\n')
  cat(t.test(val_5y, val_2y)$p.val)
  cat('\n\n')
  cat('6w vs 5y p-value\n')
  cat(t.test(val_5y, val_6m)$p.val)
  cat('\n\n')

  
  for(treatment_pos in 1:treatment_n){
    cat('{var_} tests {treatment_vals[treatment_pos]}\n' %>% f)
    val_ <- data_treats[[treatment_pos]][[var_]]
    val_6m <- data_treats[[treatment_pos]][[var_6m]]
    val_2y <- data_treats[[treatment_pos]][[var_2y]]
    val_5y <- data_treats[[treatment_pos]][[var_5y]]
    cat('\nPreop vs 6m p-value\n')
    cat(t.test(val_6m , val_)$p.val)
    cat('\n\n')
    cat('Preop vs 2y p-value\n')
    cat(t.test(val_2y, val_)$p.val)
    cat('\n\n')
    cat('Preop vs 5y p-value\n')
    cat(t.test(val_5y, val_)$p.val)
    cat('\n\n')
    cat('6m vs 2y p-value\n')
    cat(t.test(val_2y, val_6m)$p.val)
    cat('\n\n')
    cat('2y vs 5y p-value\n')
    cat(t.test(val_5y, val_2y)$p.val)
    cat('\n\n')
    cat('6m vs 5y p-value\n')
    cat(t.test(val_5y, val_6m)$p.val)
    cat('\n\n')
  }
}
```


### Change Quality of Life
```{r echo=FALSE, comment="", include=TRUE}
data_change <- data_ %>% copy
for(var_ in analysis_vars$quality ){
  var_6m <- "6M. {var_}" %>% f
  var_1y <- "1Y. {var_}" %>% f
  var_2y <- "2Y. {var_}" %>% f
  var_5y <- "5Y. {var_}" %>% f
  vars_years <- c(var_6m, var_1y, var_2y, var_5y)
  for(var_y in vars_years){
    data_change[, c(var_y) := get(var_y) - get(var_)]
  }
  data_treats_change <- list()
  for(treatment_pos in 1:treatment_n){
    data_treats_change[[treatment_pos]] <- data_change[get(treatment_) == treatment_vals[treatment_pos]]
  }
  
  for(var_y in vars_years){
    res <- stats_fun(data_change[[var_y]])
    res_treats <- list()
    for(treatment_pos in 1:treatment_n){
      res_treats[[treatment_pos]] <- stats_fun(
        data_treats_change[[treatment_pos]][[var_y]]
      )    
    }
    for( res_name in names(res) ){
      cat(var_y)
      cat(' - ')
      cat(res_name)
      cat('\n')
      
      cat('All\n')
      print(res[[res_name]])
      
    for(treatment_pos in 1:treatment_n){
      cat(treatment_vals[treatment_pos])
      cat('\n')
      print(res_treats[[treatment_pos]][[res_name]])
      cat('\n')
    }
      
      if( res_name == 'mean'){
        for(n1 in 1:(treatment_n-1)){
          for(n2 in (n1+1):treatment_n){
            p.val <- calc_p_vals(data_change, var_y, treatment_, treatment_vals[c(n1, n2)])
            if(!is.null(p.val)){
              cat('{treatment_vals[n1]} vs {treatment_vals[n2]} p-value:\n' %>% f)
              print(p.val)
              cat('\n\n')
            }
          }
        }
      }
    }
    cat('\n\n')
  }
  
  cat('{var_} tests all\n' %>% f)
  val_ <- data_change[[var_]]
  val_6m <- data_change[[var_6m]]
  val_2y <- data_change[[var_2y]]
  val_5y <- data_change[[var_5y]]
  cat('\nPreop vs 6m p-value\n')
  cat(t.test(val_6m , val_)$p.val)
  cat('\n\n')
  cat('Preop vs 2y p-value\n')
  cat(t.test(val_2y, val_)$p.val)
  cat('\n\n')
  cat('Preop vs 5y p-value\n')
  cat(t.test(val_5y, val_)$p.val)
  cat('\n\n')
  cat('6m vs 2y p-value\n')
  cat(t.test(val_2y, val_6m)$p.val)
  cat('\n\n')
  cat('2y vs 5y p-value\n')
  cat(t.test(val_5y, val_2y)$p.val)
  cat('\n\n')
  cat('6w vs 5y p-value\n')
  cat(t.test(val_5y, val_6m)$p.val)
  cat('\n\n')

  for(treatment_pos in 1:treatment_n){
    cat('{var_} tests {treatment_vals[treatment_pos]}\n' %>% f)
    val_ <- data_treats_change[[treatment_pos]][[var_]]
    val_6m <- data_treats_change[[treatment_pos]][[var_6m]]
    val_2y <- data_treats_change[[treatment_pos]][[var_2y]]
    val_5y <- data_treats_change[[treatment_pos]][[var_5y]]
    cat('\nPreop vs 6m p-value\n')
    cat(t.test(val_6m , val_)$p.val)
    cat('\n\n')
    cat('Preop vs 2y p-value\n')
    cat(t.test(val_2y, val_)$p.val)
    cat('\n\n')
    cat('Preop vs 5y p-value\n')
    cat(t.test(val_5y, val_)$p.val)
    cat('\n\n')
    cat('6m vs 2y p-value\n')
    cat(t.test(val_2y, val_6m)$p.val)
    cat('\n\n')
    cat('2y vs 5y p-value\n')
    cat(t.test(val_5y, val_2y)$p.val)
    cat('\n\n')
    cat('6m vs 5y p-value\n')
    cat(t.test(val_5y, val_6m)$p.val)
    cat('\n\n')
  }
}
```

### Surgery
```{r echo=FALSE, comment="", include=TRUE}
for(var_ in analysis_vars$surgery ){
  res <- stats_fun(data_[[var_]])
  res_treats <- list()
  for(treatment_pos in 1:treatment_n){
    res_treats[[treatment_pos]] <- stats_fun(
      data_treats[[treatment_pos]][[var_]])
  }
  for( res_name in names(res) ){
    cat(var_)
    cat(' - ')
    cat(res_name)
    cat('\n')
    
    cat('All\n')
    print(res[[res_name]])

    for(treatment_pos in 1:treatment_n){
      cat(treatment_vals[treatment_pos])
      cat('\n')
      print(res_treats[[treatment_pos]][[res_name]])
      cat('\n')
    }
    
    if( res_name == 'mean'){
      for(n1 in 1:(treatment_n-1)){
        for(n2 in (n1+1):treatment_n){
          p.val <- calc_p_vals(data_, var_, treatment_, treatment_vals[c(n1, n2)])
          if(!is.null(p.val)){
            cat('{treatment_vals[n1]} vs {treatment_vals[n2]} p-value:\n' %>% f)
            print(p.val)
            cat('\n\n')
          }
        }
      }
    }
  }
  cat('\n\n')
}
```



# Before 2Y

## Reinterventions

```{r}
res <- calc_complications_many(data_, treatment_vals, treatment_, lower_years=0, upper_years=2)
```

```{r include=TRUE}
res$number_reiqs
```

```{r include=TRUE}
res$p_vals_reiqs
```

## Impacts

```{r include=TRUE}
res$impacts
```

## Categories

```{r include=TRUE}
res$categories
```

## Categories Major Complications

```{r include=TRUE}
res$categories_major
```

## Time to surgery

```{r include=TRUE}
res$time_to_surgery$stats
```

```{r include=TRUE}
res$time_to_surgery$p_vals
```


# From 2Y - 5Y

## Reinterventions

```{r}
res <- calc_complications_many(data_, treatment_vals, treatment_, lower_years=2, upper_years=5)
```

```{r include=TRUE}
res$number_reiqs
```

```{r include=TRUE}
res$p_vals_reiqs
```

## Impacts

```{r include=TRUE}
res$impacts
```

## Categories

```{r include=TRUE}
res$categories
```

## Categories Major Complications

```{r include=TRUE}
res$categories_major
```

## Time to surgery

```{r include=TRUE}
res$time_to_surgery$stats
```

```{r include=TRUE}
res$time_to_surgery$p_vals
```


# Before 5Y

## Reinterventions

```{r}
res <- calc_complications_many(data_, treatment_vals, treatment_, lower_years=0, upper_years=5)
```

```{r include=TRUE}
res$number_reiqs
```

```{r include=TRUE}
res$p_vals_reiqs
```

## Impacts

```{r include=TRUE}
res$impacts
```

## Categories

```{r include=TRUE}
res$categories
```

## Categories Major Complications

```{r include=TRUE}
res$categories_major
```

## Time to surgery

```{r include=TRUE}
res$time_to_surgery$stats
```

```{r include=TRUE}
res$time_to_surgery$p_vals
```
