---
title: "Descriptive Stats"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_knit$set(
  echo = TRUE, 
  root.dir=normalizePath('../')
)
```

```{r echo=FALSE, warning=FALSE, include=FALSE}
library(readxl)
library(data.table)
library(magrittr)
library(yaml)
library(glue)
f <- glue

xls_path <- 'data/ESSG extraction December 2020 - DEF.xlsx'

clinical_data <- read_excel(xls_path) %>% 
  as.data.table()

setnames(
  clinical_data, 
  'SRS22 -SI_First Visit', 
  'SRS22 - Self image / Appearance_First Visit'
)
setnames(
  clinical_data, 
  'SRS22 - MH_First Visit', 
  'SRS22 - Mental health_First Visit'
)
setnames(
  clinical_data, 
  'SRS22 - Function_First Visit', 
  'SRS22 - Function / Activity_First Visit'
)

clinical_data[, 
  `Pelvic Fixation` := grepl(
    'Iliac', 
    `Posterior Instrumented Fusion: Upper / Lower Levels`, 
    fixed=TRUE
  )] %>% 
  .[, `Pelvic Fixation` := ifelse(`Pelvic Fixation` == TRUE, 'Yes', 'No')]


vars <- read_yaml('code/descriptive.yml')

stats_fun <- function(variable){
  if( class(variable) == 'numeric' ){
    return( list(
      mean = mean(variable, na.rm=TRUE),
      sd = sd(variable, na.rm = TRUE)
    ))
  }else{
    res_table <- table(variable)
    return(list(
      table = res_table, 
      proportion = prop.table(res_table)
    ))
  }
}

```

## Filters
```{r}
clinical_data %<>% 
  .[as.Date(`st1. Date of Stage 1`) < as.Date('2018-12-15')] %>% 
  .[ALIF + TLIF + PLIF > 0] %>% 
  .[`Posterior Instrumented Fusion`!='No'] %>% 
  .[, Alif := ifelse(ALIF > 0, 'Yes', 'No')]

alif_data <- clinical_data %>% 
  .[!is.na(`2 YEAR VISIT - Date of visit`) | !is.na(`3 YEAR VISIT - Date of visit`)]

total_patients <- clinical_data[, `Code of the patient` %>% uniqueN]
patients_visited <- alif_data[, `Code of the patient` %>% uniqueN]
patients_visited_6w <- clinical_data %>% 
  .[!is.na(`6 WEEKS VISIT - Date of visit`), `Code of the patient` %>% uniqueN]
```

- Number of Patients with 'st1. Date of Stage 1' < '2018-12-15': `r total_patients`
- Number of patients with visit in 6 weeks: `r patients_visited_6w`
- Number of patients with visit in 2 or 3 years: `r patients_visited`


```{r echo=FALSE}
calc_p_vals <- function(dt, var_){
  vals_n <- dt[, get(var_)] %>% uniqueN
  if(class(dt[, get(var_)]) == 'numeric'){
    p.val <- t.test(
      dt[Alif=='Yes', get(var_)],
      dt[Alif=='No', get(var_)]
    )$p.val
  }else if(vals_n == 2){
    t1 <- table(dt[Alif=='Yes', get(var_)])
    t2 <- table(dt[Alif=='No', get(var_)])
    
    p.val <- prop.test(rbind(t1, t2))$p.val
  }else{
    p.val <- NULL
  }
  
  return(p.val)
}

```




### Demographics
```{r echo=FALSE, comment=""}
for(var_ in vars$demographics ){
  cat(var_)
  cat('\n')
  
  cat('All\n')
  res <- stats_fun(alif_data[, get(var_)])
  for( res_name in names(res) ){
    print(res_name)
    print(res[[res_name]])
  }
  cat('\n\n')
  
  cat('Alif\n')
  res <- stats_fun(alif_data[Alif=='Yes', get(var_)])
  for( res_name in names(res) ){
    print(res_name)
    print(res[[res_name]])
  }
  cat('\n\n')
  
  cat('Plif/Tlif\n')
  res <- stats_fun(alif_data[Alif=='No', get(var_)])
  for( res_name in names(res) ){
    print(res_name)
    print(res[[res_name]])
  }
  cat('\n\n')
  
  p.val <- calc_p_vals(alif_data, var_)
  if(!is.null(p.val)){
    cat('Alif vs Plif/Tlif p-value:\n')
    print(p.val)
    cat('\n\n')
  }
}
```


### Radiology
```{r echo=FALSE, comment=""}
for(var_ in vars$radiology ){
  var_2y <- "2Y. {var_}" %>% f
  var_5y <- "5Y. {var_}" %>% f
  vars_years <- c(var_, var_2y, var_5y)
  for(var_y in vars_years){
    cat(var_y)
    cat('\n')
    
    cat('All\n')
    res <- stats_fun(alif_data[, get(var_y)])
    for( res_name in names(res) ){
      print(res_name)
      print(res[[res_name]])
    }
    cat('\n\n')
    
    cat('Alif\n')
    res <- stats_fun(alif_data[Alif=='Yes', get(var_y)])
    for( res_name in names(res) ){
      print(res_name)
      print(res[[res_name]])
    }
    cat('\n\n')
    
    cat('Plif/Tlif\n')
    res <- stats_fun(alif_data[Alif=='No', get(var_y)])
    for( res_name in names(res) ){
      print(res_name)
      print(res[[res_name]])
    }
    cat('\n\n')
    
    p.val <- calc_p_vals(alif_data, var_y)
    if(!is.null(p.val)){
      cat('Alif vs Plif/Tlif p-value:\n')
      print(p.val)
      cat('\n\n')
    }
  }
}
```


### Quality of Life
```{r echo=FALSE, comment=""}
for(var_0 in vars$quality ){
  var_ <- "{var_0}_First Visit" %>% f
  var_2y <- "2Y. {var_0}" %>% f
  var_5y <- "5Y. {var_0}" %>% f
  vars_years <- c(var_, var_2y, var_5y)
  for(var_y in vars_years){
    cat(var_y)
    cat('\n')
    
    cat('All\n')
    res <- stats_fun(alif_data[, get(var_y)])
    for( res_name in names(res) ){
      print(res_name)
      print(res[[res_name]])
    }
    cat('\n\n')
    
    cat('Alif\n')
    res <- stats_fun(alif_data[Alif=='Yes', get(var_y)])
    for( res_name in names(res) ){
      print(res_name)
      print(res[[res_name]])
    }
    cat('\n\n')
    
    cat('Plif/Tlif\n')
    res <- stats_fun(alif_data[Alif=='No', get(var_y)])
    for( res_name in names(res) ){
      print(res_name)
      print(res[[res_name]])
    }
    cat('\n\n')
    
    p.val <- calc_p_vals(alif_data, var_y)
    if(!is.null(p.val)){
      cat('Alif vs Plif/Tlif p-value:\n')
      print(p.val)
      cat('\n\n')
    }

  }
}
```


### Surgery
```{r echo=FALSE, comment=""}
for(var_ in vars$surgery ){
  cat(var_)
  cat('\n')
  
  cat('All\n')
  res <- stats_fun(alif_data[, get(var_)])
  for( res_name in names(res) ){
    print(res_name)
    print(res[[res_name]])
  }
  cat('\n\n')
  
  cat('Alif\n')
  res <- stats_fun(alif_data[Alif=='Yes', get(var_)])
  for( res_name in names(res) ){
    print(res_name)
    print(res[[res_name]])
  }
  cat('\n\n')
  
  cat('Plif/Tlif\n')
  res <- stats_fun(alif_data[Alif=='No', get(var_)])
  for( res_name in names(res) ){
    print(res_name)
    print(res[[res_name]])
  }
  cat('\n\n')
  
  p.val <- calc_p_vals(alif_data, var_)
  if(!is.null(p.val)){
    cat('Alif vs Plif/Tlif p-value:\n')
    print(p.val)
    cat('\n\n')
  }

}
```
