---
title: "Clusters Descriptives"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, include=FALSE, message=FALSE, warning=FALSE, comment="")
```

```{r}
library(data.table)
library(magrittr)
library(yaml)
library(stats)
library(rpart)
library(rattle)

source('patient_selection.R')
```

```{r, message=FALSE}
data_ <- get_data_base()
cluster_vars <- read_yaml('cluster_vars.yml')
analysis_vars <- read_yaml('descriptive.yml')
cluster_num <- 3
```

```{r include=TRUE}
print(cluster_vars)
```



```{r echo=TRUE}
data_ %>% 
  .[followup_2y==TRUE] %>%
  .[`st1. Date of Stage` %>% as.Date() < as.Date('2015-09-01')] %>%
  .[Study=='Op'] %>% 
  .[Site != 'ANK Op'] %>% 
  .[`Vital status` == 'Alive'] -> 
  data_
```
Initial Patients: `r data_[, .N]`

```{r, message=FALSE}
data_ %>% 
  .[, .SD, .SDcols = cluster_vars$vars] %>% 
  scale %>% 
  dist %>% 
  hclust(method="ward.D2") ->
  clusters

data_[, cluster := as.factor(cutree(clusters,k=cluster_num))]
```

Number of patients
```{r include=TRUE}
data_[, .N, cluster]
```



```{r}
treatment_ <- 'cluster'
treatment_vals <- data_[, levels(cluster)]
treatments_n <- len(treatment_vals)
```

```{r}
data_treats <- list()
for(val_ in treatment_vals){
  data_treats[[val_]] <- data_[get(treatment_) == val_]
}
```

## Statistics

### ODI

ODI stats overall

```{r include=TRUE}
data_[, .(
  mean=mean(`ODI - Score (%)`, na.rm=TRUE),
  sd = sd(`ODI - Score (%)`, na.rm=TRUE))]
```

ODI stats by cluster

```{r include=TRUE}
data_[, .(
  mean=mean(`ODI - Score (%)`, na.rm=TRUE),
  sd = sd(`ODI - Score (%)`, na.rm=TRUE)),
  cluster]
```


### 3CO: all vs each cluster

```{r include=TRUE}
prop_3co <- c()
for(val_ in treatment_vals){
  cluster_yes <- data_treats[[val_]][, sum(`3CO` == 'Yes')]
  cluster_n <- data_treats[[val_]][, .N]
  total_yes <- data_[, sum(`3CO` == 'Yes')]
  total_n <- data_[, .N]
  prop_3co %<>% c(prop.test(c(cluster_yes, total_yes), c(cluster_n, total_n))$p.val)
}

data.table(cluster=treatment_vals, p.val = prop_3co)
```

### Pelvic fixation: all vs each cluster

```{r include=TRUE}
prop_pf <- c()
for(val_ in treatment_vals){
  cluster_yes <- data_treats[[val_]][, sum(`Pelvic fixation` == 'Yes')]
  cluster_n <- data_treats[[val_]][, .N]
  total_yes <- data_[, sum(`Pelvic fixation` == 'Yes')]
  total_n <- data_[, .N]
  prop_pf %<>% c(prop.test(c(cluster_yes, total_yes), c(cluster_n, total_n))$p.val)
}

data.table(cluster=treatment_vals, p.val = prop_pf)
```

### P-valor ASA 1 cluster vs cluster
```{r include=TRUE}
var_ <- "ASA classification"
data_[, .(
  treatment=get(treatment_), variable=get(var_))] ->
  data__

data__[, variable := ifelse(as.character(variable) == 1, 1, 2)]
res <- data__[, .(asa_1 = sum(variable == 1), .N), treatment] %>% 
  .[!is.na(treatment)]

print(res)
```


```{r include=TRUE}
n1 <- 1
n2 <- 2
print("P-values Treatment {treatment_vals[n1]} vs Treatment {treatment_vals[n2]}" %>% f)
prop.test(
  c(
    res[treatment==treatment_vals[n1]]$asa_1,
    res[treatment==treatment_vals[n2]]$asa_1
  ),
  c(
    res[treatment==treatment_vals[n1]]$N,
    res[treatment==treatment_vals[n2]]$N
  ))$p.val
```

```{r include=TRUE}
n1 <- 1
n2 <- 3
print("P-values Treatment {treatment_vals[n1]} vs Treatment {treatment_vals[n2]}" %>% f)
prop.test(
  c(
    res[treatment==treatment_vals[n1]]$asa_1,
    res[treatment==treatment_vals[n2]]$asa_1
  ),
  c(
    res[treatment==treatment_vals[n1]]$N,
    res[treatment==treatment_vals[n2]]$N
  ))$p.val
```

```{r include=TRUE}
n1 <- 2
n2 <- 3
print("P-values Treatment {treatment_vals[n1]} vs Treatment {treatment_vals[n2]}" %>% f)
prop.test(
  c(
    res[treatment==treatment_vals[n1]]$asa_1,
    res[treatment==treatment_vals[n2]]$asa_1
  ),
  c(
    res[treatment==treatment_vals[n1]]$N,
    res[treatment==treatment_vals[n2]]$N
  ))$p.val
```

### P-valor ASA 3 cluster vs cluster
```{r include=TRUE}
var_ <- "ASA classification"
data_[, .(
  treatment=get(treatment_), variable=get(var_))] ->
  data__

data__[, variable := ifelse(as.character(variable) == 3, 1, 2)]
res <- data__[, .(asa_3 = sum(variable == 1), .N), treatment] %>% 
  .[!is.na(treatment)]

print(res)
```


```{r include=TRUE}
n1 <- 1
n2 <- 2
print("P-values Treatment {treatment_vals[n1]} vs Treatment {treatment_vals[n2]}" %>% f)
prop.test(
  c(
    res[treatment==treatment_vals[n1]]$asa_3,
    res[treatment==treatment_vals[n2]]$asa_3
  ),
  c(
    res[treatment==treatment_vals[n1]]$N,
    res[treatment==treatment_vals[n2]]$N
  ))$p.val
```

```{r include=TRUE}
n1 <- 1
n2 <- 3
print("P-values Treatment {treatment_vals[n1]} vs Treatment {treatment_vals[n2]}" %>% f)
prop.test(
  c(
    res[treatment==treatment_vals[n1]]$asa_3,
    res[treatment==treatment_vals[n2]]$asa_3
  ),
  c(
    res[treatment==treatment_vals[n1]]$N,
    res[treatment==treatment_vals[n2]]$N
  ))$p.val
```

```{r include=TRUE}
n1 <- 2
n2 <- 3
print("P-values Treatment {treatment_vals[n1]} vs Treatment {treatment_vals[n2]}" %>% f)
prop.test(
  c(
    res[treatment==treatment_vals[n1]]$asa_3,
    res[treatment==treatment_vals[n2]]$asa_3
  ),
  c(
    res[treatment==treatment_vals[n1]]$N,
    res[treatment==treatment_vals[n2]]$N
  ))$p.val
```


### P-valor Prior Spine Surgery Yes cluster vs cluster
```{r include=TRUE}
var_ <- "Prior Spine Surgery"
data_[, .(
  treatment=get(treatment_), variable=get(var_))] ->
  data__

res <- data__[, .(prior_yes = sum(variable == 'Yes'), .N), treatment] %>% 
  .[!is.na(treatment)]

print(res)
```

  
```{r include=TRUE}
n1 <- 1
n2 <- 2
print("P-values Treatment {treatment_vals[n1]} vs Treatment {treatment_vals[n2]}" %>% f)
prop.test(
  c(
    res[treatment==treatment_vals[n1]]$prior_yes,
    res[treatment==treatment_vals[n2]]$prior_yes
  ),
  c(
    res[treatment==treatment_vals[n1]]$N,
    res[treatment==treatment_vals[n2]]$N
  ))$p.val
```

```{r include=TRUE}
n1 <- 1
n2 <- 3
print("P-values Treatment {treatment_vals[n1]} vs Treatment {treatment_vals[n2]}" %>% f)
prop.test(
  c(
    res[treatment==treatment_vals[n1]]$prior_yes,
    res[treatment==treatment_vals[n2]]$prior_yes
  ),
  c(
    res[treatment==treatment_vals[n1]]$N,
    res[treatment==treatment_vals[n2]]$N
  ))$p.val
```

```{r include=TRUE}
n1 <- 2
n2 <- 3
print("P-values Treatment {treatment_vals[n1]} vs Treatment {treatment_vals[n2]}" %>% f)
prop.test(
  c(
    res[treatment==treatment_vals[n1]]$prior_yes,
    res[treatment==treatment_vals[n2]]$prior_yes
  ),
  c(
    res[treatment==treatment_vals[n1]]$N,
    res[treatment==treatment_vals[n2]]$N
  ))$p.val
```


### 3CO cluster vs cluster

```{r include=TRUE}
var_ <- "3CO"
data_[, .(
  treatment=get(treatment_), variable=get(var_))] ->
  data__

res <- data__[, .(prior_yes = sum(variable == 'Yes'), .N), treatment] %>% 
  .[!is.na(treatment)]

print(res)
```

  
```{r include=TRUE}
n1 <- 1
n2 <- 2
print("P-values Treatment {treatment_vals[n1]} vs Treatment {treatment_vals[n2]}" %>% f)
prop.test(
  c(
    res[treatment==treatment_vals[n1]]$prior_yes,
    res[treatment==treatment_vals[n2]]$prior_yes
  ),
  c(
    res[treatment==treatment_vals[n1]]$N,
    res[treatment==treatment_vals[n2]]$N
  ))$p.val
```

```{r include=TRUE}
n1 <- 1
n2 <- 3
print("P-values Treatment {treatment_vals[n1]} vs Treatment {treatment_vals[n2]}" %>% f)
prop.test(
  c(
    res[treatment==treatment_vals[n1]]$prior_yes,
    res[treatment==treatment_vals[n2]]$prior_yes
  ),
  c(
    res[treatment==treatment_vals[n1]]$N,
    res[treatment==treatment_vals[n2]]$N
  ))$p.val
```

```{r include=TRUE}
n1 <- 2
n2 <- 3
print("P-values Treatment {treatment_vals[n1]} vs Treatment {treatment_vals[n2]}" %>% f)
prop.test(
  c(
    res[treatment==treatment_vals[n1]]$prior_yes,
    res[treatment==treatment_vals[n2]]$prior_yes
  ),
  c(
    res[treatment==treatment_vals[n1]]$N,
    res[treatment==treatment_vals[n2]]$N
  ))$p.val
```


### Pelvic Fixation cluster vs cluster

```{r include=TRUE}
var_ <- "Pelvic fixation"
data_[, .(
  treatment=get(treatment_), variable=get(var_))] ->
  data__

res <- data__[, .(prior_yes = sum(variable == 'Yes'), .N), treatment] %>% 
  .[!is.na(treatment)]

print(res)
```

  
```{r include=TRUE}
n1 <- 1
n2 <- 2
print("P-values Treatment {treatment_vals[n1]} vs Treatment {treatment_vals[n2]}" %>% f)
prop.test(
  c(
    res[treatment==treatment_vals[n1]]$prior_yes,
    res[treatment==treatment_vals[n2]]$prior_yes
  ),
  c(
    res[treatment==treatment_vals[n1]]$N,
    res[treatment==treatment_vals[n2]]$N
  ))$p.val
```

```{r include=TRUE}
n1 <- 1
n2 <- 3
print("P-values Treatment {treatment_vals[n1]} vs Treatment {treatment_vals[n2]}" %>% f)
prop.test(
  c(
    res[treatment==treatment_vals[n1]]$prior_yes,
    res[treatment==treatment_vals[n2]]$prior_yes
  ),
  c(
    res[treatment==treatment_vals[n1]]$N,
    res[treatment==treatment_vals[n2]]$N
  ))$p.val
```

```{r include=TRUE}
n1 <- 2
n2 <- 3
print("P-values Treatment {treatment_vals[n1]} vs Treatment {treatment_vals[n2]}" %>% f)
prop.test(
  c(
    res[treatment==treatment_vals[n1]]$prior_yes,
    res[treatment==treatment_vals[n2]]$prior_yes
  ),
  c(
    res[treatment==treatment_vals[n1]]$N,
    res[treatment==treatment_vals[n2]]$N
  ))$p.val
```


### Quality of Life change with respect baseline
```{r echo=FALSE, comment="", include=TRUE}
data_change <- data_ %>% copy
for(var_ in analysis_vars$quality ){
  var_6m <- "6M. {var_}" %>% f
  var_1y <- "1Y. {var_}" %>% f
  var_2y <- "2Y. {var_}" %>% f
  var_5y <- "5Y. {var_}" %>% f
  vars_years <- c(var_6m, var_1y, var_2y, var_5y)
  res_vars_num <- list()
  res_treats <- list()
  for(var_y in vars_years){
    data_change[, c(var_y) := get(var_y) - get(var_)]
    res_treats[['All']] <- stats_fun(data_change[[var_y]], effect_size=TRUE)
    for(val_ in treatment_vals){
      res_treats[[val_]] <- stats_fun(data_change[get(treatment_) == val_][[var_y]],
        effect_size=TRUE)
    }

    p_vals_list <- list()
    for(val_1_pos in 1:(treatments_n - 1)){
      val_1 <- treatment_vals[val_1_pos]
      p_vals_list[[val_1]] <- list()
      for(val_2_pos in (val_1_pos+1):treatments_n){
        val_2 <- treatment_vals[val_2_pos]
        p.val <- calc_p_vals(data_change, var_y, treatment_, c(val_1, val_2)) %>%
          round(4)
        if( is.null(p.val) ) p.val <- NA
        p_vals_list[["p.val_{val_1}" %>% f]][[val_2]] <- p.val
      }

      p.val <- calc_p_vals(
          data_change, var_y, treatment_, c(val_1, 'all')
        ) %>% round(4)
      if( is.null(p.val) ) p.val <- NA
      p_vals_list[["p.val_{val_1}" %>% f]][['all']] <- p.val
    }
    
    val_1 <- treatment_vals[treatments_n]
    p.val <- calc_p_vals(
          data_change, var_y, treatment_, c(val_1, 'all')
        ) %>% round(4)
    if( is.null(p.val) ) p.val <- NA
    p_vals_list[["p.val_{val_1}" %>% f]][['all']] <- p.val
    
    for(treat_ in treatment_vals){
      p.val <- calc_p_vals(data_change, var_y, treatment_, treat_and_co = treat_) %>% 
          round(4)
        p_vals_list[["p.val_{treat_}" %>% f]][['vs_the_rest']] <- p.val
    }

    res_vars_num[[var_y]] <- cbind(
      res_treats %>% unlist %>% t %>% as.data.frame(),
      p_vals_list %>% unlist %>% t %>% as.data.frame()
    )

    formula_ <- "`{var_y}`~cluster" %>% f %>% as.formula
    aov_res <- aov(formula_, data_change)
    res_vars_num[[var_y]]$p.val_all <- summary(aov_res)[[1]][["Pr(>F)"]][1] %>%
      round(4)
  }

  cat('\n\n\n')
  print(var_)
  cat('\n')
  print(do.call(rbind, res_vars_num))

}
```