---
title: "Pelvis UT vs Pelvis LT"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, include=FALSE, message=FALSE, warning=FALSE, comment="")
```

```{r}
library(data.table)
library(magrittr)
library(yaml)

source('patient_selection.R')
```

```{r, message=FALSE}
analysis_vars <- read_yaml('descriptive.yml')
data_ <- get_data()
```
Initial Patients: `r data_[, .N]`

```{r}
data_ %<>% .[`Posterior Instrumented Fusion` == 'Yes']
```
With Posterior Instrumented Fusion: `r data_[, .N]`

```{r}
data_[, `Posterior Instrumented Fusion: Upper / Lower Levels`] %>% 
  sapply(. %>% strsplit('-') %>% .[[1]] %>% .[2]) ->
  post_intr_fusion

data_ %<>% .[post_intr_fusion == 'Iliac']
```
Posterior Instrumental Fusion is Iliac: `r data_[, .N]`

- Upper Thoracic (UT): T1-T9-Pelvis
- Lower Thoracic (LT): T10-T12- Iliac
```{r include=TRUE}
data_[, `Posterior Instrumented Fusion: Upper / Lower Levels`] %>% 
  sapply(. %>% strsplit('-') %>% .[[1]] %>% .[1]) ->
  post_intr_fusion

UT <- paste("T", 1:9, sep="")
LT <- paste("T", 10:12, sep="")

data_[post_intr_fusion %chin% UT, thoracic_type := 'UT']
data_[post_intr_fusion %chin% LT, thoracic_type := 'LT']

data_[, .N, thoracic_type]
```

```{r}
treatment_ <- 'thoracic_type'
treatment_vals <- c('UT', 'LT')
```

```{r}
data_1 <- data_[get(treatment_) == treatment_vals[1]]
data_2 <- data_[get(treatment_) == treatment_vals[2]]
```


### Demographics
```{r echo=FALSE, comment="", include=TRUE}
for(var_ in analysis_vars$demographics ){
  
  res <- stats_fun(data_[[var_]])
  res_1 <- stats_fun(data_1[[var_]])
  res_2 <- stats_fun(data_2[[var_]])
  for( res_name in names(res) ){
    cat(var_)
    cat(' - ')
    cat(res_name)
    cat('\n')
    
    cat('All\n')
    print(res[[res_name]])

    cat(treatment_vals[1])
    cat('\n')
    print(res_1[[res_name]])
    
    cat(treatment_vals[2])
    cat('\n')
    print(res_2[[res_name]])
    cat('\n')
    
    p.val <- calc_p_vals(data_, var_, treatment_, treatment_vals)
    if(!is.null(p.val)){
      cat('{treatment_vals[1]} vs {treatment_vals[2]} p-value:\n' %>% f)
      print(p.val)
      cat('\n\n')
    }
  }
  cat('\n\n')
}
```


### Radiology
```{r echo=FALSE, comment="", include=TRUE}
for(var_ in analysis_vars$radiology ){
  var_6w <- "6W. {var_}" %>% f
  var_2y <- "2Y. {var_}" %>% f
  var_5y <- "5Y. {var_}" %>% f
  vars_years <- c(var_, var_6w, var_2y, var_5y)
  for(var_y in vars_years){
    res <- stats_fun(data_[[var_y]])
    res_1 <- stats_fun(data_1[[var_y]])
    res_2 <- stats_fun(data_2[[var_y]])
    for( res_name in names(res) ){
      cat(var_)
      cat(' - ')
      cat(res_name)
      cat('\n')
      
      cat('All\n')
      print(res[[res_name]])
      
      cat(treatment_vals[1])
      cat('\n')
      print(res_1[[res_name]])
      
      cat(treatment_vals[2])
      cat('\n')
      print(res_2[[res_name]])
      cat('\n')
      
      p.val <- calc_p_vals(data_, var_, treatment_, treatment_vals)
      if(!is.null(p.val)){
        cat('{treatment_vals[1]} vs {treatment_vals[2]} p-value:\n' %>% f)
        print(p.val)
        cat('\n\n')
      }
    }
    cat('\n\n')
  }
    
  cat('{var_} tests all\n' %>% f)
  val_ <- data_[[var_]]
  val_6w <- data_[[var_6w]]
  val_2y <- data_[[var_2y]]
  val_5y <- data_[[var_5y]]
  cat('\nPreop vs 6w p-value\n')
  cat(t.test(val_6w , val_)$p.val)
  cat('\n\n')
  cat('Preop vs 2y p-value\n')
  cat(t.test(val_2y, val_)$p.val)
  cat('\n\n')
  cat('Preop vs 5y p-value\n')
  cat(t.test(val_5y, val_)$p.val)
  cat('\n\n')
  cat('6w vs 2y p-value\n')
  cat(t.test(val_2y, val_6w)$p.val)
  cat('\n\n')
  cat('2y vs 5y p-value\n')
  cat(t.test(val_5y, val_2y)$p.val)
  cat('\n\n')
  
  cat('{var_} tests {treatment_vals[1]}\n' %>% f)
  val_ <- data_1[[var_]]
  val_6w <- data_1[[var_6w]]
  val_2y <- data_1[[var_2y]]
  val_5y <- data_1[[var_5y]]
  cat('\nPreop vs 6w p-value\n')
  cat(t.test(val_6w , val_)$p.val)
  cat('\n\n')
  cat('Preop vs 2y p-value\n')
  cat(t.test(val_2y, val_)$p.val)
  cat('\n\n')
  cat('Preop vs 5y p-value\n')
  cat(t.test(val_5y, val_)$p.val)
  cat('\n\n')
  cat('6w vs 2y p-value\n')
  cat(t.test(val_2y, val_6w)$p.val)
  cat('\n\n')
  cat('2y vs 5y p-value\n')
  cat(t.test(val_5y, val_2y)$p.val)
  cat('\n\n')
  
  cat('{var_} tests {treatment_vals[2]}\n' %>% f)
  val_ <- data_2[[var_]]
  val_6w <- data_2[[var_6w]]
  val_2y <- data_2[[var_2y]]
  val_5y <- data_2[[var_5y]]
  cat('\nPreop vs 6w p-value\n')
  cat(t.test(val_6w , val_)$p.val)
  cat('\n\n')
  cat('Preop vs 2y p-value\n')
  cat(t.test(val_2y, val_)$p.val)
  cat('\n\n')
  cat('Preop vs 5y p-value\n')
  cat(t.test(val_5y, val_)$p.val)
  cat('\n\n')
  cat('6w vs 2y p-value\n')
  cat(t.test(val_2y, val_6w)$p.val)
  cat('\n\n')
  cat('2y vs 5y p-value\n')
  cat(t.test(val_5y, val_2y)$p.val)
  cat('\n\n')
}
```


### Quality of Life
```{r echo=FALSE, comment="", include=TRUE}
for(var_ in analysis_vars$quality ){
  var_6m <- "6M. {var_}" %>% f
  var_2y <- "2Y. {var_}" %>% f
  var_5y <- "5Y. {var_}" %>% f
  vars_years <- c(var_, var_2y, var_5y)
  for(var_y in vars_years){
    res <- stats_fun(data_[[var_y]])
    res_1 <- stats_fun(data_1[[var_y]])
    res_2 <- stats_fun(data_2[[var_y]])
    for( res_name in names(res) ){
      cat(var_)
      cat(' - ')
      cat(res_name)
      cat('\n')
      
      cat('All\n')
      print(res[[res_name]])
      
      cat(treatment_vals[1])
      cat('\n')
      print(res_1[[res_name]])
      
      cat(treatment_vals[2])
      cat('\n')
      print(res_2[[res_name]])
      cat('\n')
      
      p.val <- calc_p_vals(data_, var_, treatment_, treatment_vals)
      if(!is.null(p.val)){
        cat('{treatment_vals[1]} vs {treatment_vals[2]} p-value:\n' %>% f)
        print(p.val)
        cat('\n\n')
      }
    }
    cat('\n\n')
  }
  
  cat('{var_} tests all\n' %>% f)
  val_ <- data_[[var_]]
  val_6w <- data_[[var_6w]]
  val_2y <- data_[[var_2y]]
  val_5y <- data_[[var_5y]]
  cat('\nPreop vs 6w p-value\n')
  cat(t.test(val_6w , val_)$p.val)
  cat('\n\n')
  cat('Preop vs 2y p-value\n')
  cat(t.test(val_2y, val_)$p.val)
  cat('\n\n')
  cat('Preop vs 5y p-value\n')
  cat(t.test(val_5y, val_)$p.val)
  cat('\n\n')
  cat('6w vs 2y p-value\n')
  cat(t.test(val_2y, val_6w)$p.val)
  cat('\n\n')
  cat('2y vs 5y p-value\n')
  cat(t.test(val_5y, val_2y)$p.val)
  cat('\n\n')
  
  cat('{var_} tests {treatment_vals[1]}\n' %>% f)
  val_ <- data_1[[var_]]
  val_6w <- data_1[[var_6w]]
  val_2y <- data_1[[var_2y]]
  val_5y <- data_1[[var_5y]]
  cat('\nPreop vs 6w p-value\n')
  cat(t.test(val_6w , val_)$p.val)
  cat('\n\n')
  cat('Preop vs 2y p-value\n')
  cat(t.test(val_2y, val_)$p.val)
  cat('\n\n')
  cat('Preop vs 5y p-value\n')
  cat(t.test(val_5y, val_)$p.val)
  cat('\n\n')
  cat('6w vs 2y p-value\n')
  cat(t.test(val_2y, val_6w)$p.val)
  cat('\n\n')
  cat('2y vs 5y p-value\n')
  cat(t.test(val_5y, val_2y)$p.val)
  cat('\n\n')
  
  cat('{var_} tests {treatment_vals[2]}\n' %>% f)
  val_ <- data_2[[var_]]
  val_6w <- data_2[[var_6w]]
  val_2y <- data_2[[var_2y]]
  val_5y <- data_2[[var_5y]]
  cat('\nPreop vs 6w p-value\n')
  cat(t.test(val_6w , val_)$p.val)
  cat('\n\n')
  cat('Preop vs 2y p-value\n')
  cat(t.test(val_2y, val_)$p.val)
  cat('\n\n')
  cat('Preop vs 5y p-value\n')
  cat(t.test(val_5y, val_)$p.val)
  cat('\n\n')
  cat('6w vs 2y p-value\n')
  cat(t.test(val_2y, val_6w)$p.val)
  cat('\n\n')
  cat('2y vs 5y p-value\n')
  cat(t.test(val_5y, val_2y)$p.val)
  cat('\n\n')
}
```


### Surgery
```{r echo=FALSE, comment="", include=TRUE}
for(var_ in analysis_vars$surgery ){
  res <- stats_fun(data_[[var_]])
  res_1 <- stats_fun(data_1[[var_]])
  res_2 <- stats_fun(data_2[[var_]])
  for( res_name in names(res) ){
    cat(var_)
    cat(' - ')
    cat(res_name)
    cat('\n')
    
    cat('All\n')
    print(res[[res_name]])

    cat(treatment_vals[1])
    cat('\n')
    print(res_1[[res_name]])
    
    cat(treatment_vals[2])
    cat('\n')
    print(res_2[[res_name]])
    cat('\n')
    
    p.val <- calc_p_vals(data_, var_, treatment_, treatment_vals)
    if(!is.null(p.val)){
      cat('{treatment_vals[1]} vs {treatment_vals[2]} p-value:\n' %>% f)
      print(p.val)
      cat('\n\n')
    }
  }
  cat('\n\n')
}
```


### Complications 
```{r}
selected_patients <- data_[, `Code of the patient` %>% unique]

complication_data <- read_excel(xls_path, sheet = 'Complications') %>% 
  as.data.table() %>% 
  .[`Code of the patient` %chin% selected_patients]

number_reiqs <- complication_data[`Reoperation Due to Complication` =='Yes', .N]
```

Number of reinterventions: `r number_reiqs`

```{r include=TRUE}
complication_data[, .N, `Complication Impact`]
```

```{r include=TRUE}
complication_data[, .N, `Category of the complication`]
```

### Complications `r treatment_vals[1]`
```{r}
selected_patients <- data_[get(treatment_) == treatment_vals[1], `Code of the patient` %>% unique]

complication_data <- read_excel(xls_path, sheet = 'Complications') %>% 
  as.data.table() %>% 
  .[`Code of the patient` %chin% selected_patients]

number_reiqs <- complication_data[`Reoperation Due to Complication` =='Yes', .N]
```

Number of reinterventions: `r number_reiqs`

```{r include=TRUE}
complication_data[, .N, `Complication Impact`]
```

```{r include=TRUE}
complication_data[, .N, `Category of the complication`]
```

### Complications `r treatment_vals[2]`
```{r}
selected_patients <- data_[get(treatment_) == treatment_vals[2], `Code of the patient` %>% unique]

complication_data <- read_excel(xls_path, sheet = 'Complications') %>% 
  as.data.table() %>% 
  .[`Code of the patient` %chin% selected_patients]

number_reiqs <- complication_data[`Reoperation Due to Complication` =='Yes', .N]
```

Number of reinterventions: `r number_reiqs`

```{r include=TRUE}
complication_data[, .N, `Complication Impact`]
```

```{r include=TRUE}
complication_data[, .N, `Category of the complication`]
```



