---
title: "ALIF EXPLORATION"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_knit$set(
  echo = TRUE, 
  root.dir=normalizePath('../../')
)
```

```{r warning=FALSE, include=FALSE}
library(data.table)
library(magrittr)
library(kableExtra)
library(zeallot)
library(yaml)


source('code/alif/alif-utils.R')
source('code/propensity-utils.R')

tuneLenghtPropensity <- 25
modelsPropensity <- c('elastic')
tuneLenghtATE <- 15
modelsATE <- c('elastic', 'boosting')
replicas_boot <- 50L

c(sel_data, matching_vars) %<-% get_data(evaluation=TRUE)
covariates_data <- sel_data[, .SD, .SDcols=matching_vars$covariates]
treatment_name <- 'Alif'
```

### Selected Variables

```{r echo=FALSE, comment=""}
cat(matching_vars %>% as.yaml)
```

```{r echo=FALSE, warning=FALSE, results="asis"}
explore_vars(covariates_data, treatment_name=treatment_name)
```


## Propensity Scores Common Support
```{r echo=FALSE, warning=FALSE}
prop_data <- copy(covariates_data)
prop_data[['patient_id']] <- sel_data[, `Code of the patient`]
run_propensity(
  prop_data,
  treatment_name=treatment_name,
  tuneLength = tuneLenghtPropensity,
  models = modelsPropensity
) -> best_model

```

#### Model Stats

- Treatment proportion: `r mean(covariates_data[[treatment_name]] == 'Yes') %>% round(3)`
- Model Type: `r best_model$sel_model`
- Accuracy: `r best_model$accuracy`
- Params: `r as.yaml(best_model$params)`


```{r echo=FALSE}
print(best_model$plot)
```

## Model Coefficients

Bootstraping replicas: `r replicas_boot`

```{r echo=FALSE, fig.height=9, fig.width=10}
plot_coefs(treatment_name, covariates_data, best_model, replicas_boot) %>% 
  print
```


```{r echo=FALSE}
propensities <- best_model$clean_data %>% 
  .[, .(patient_id, Propensity)] %>% 
  setnames("patient_id", "Code of the patient")

sel_data %>% 
  merge(propensities, by='Code of the patient', all.x=TRUE) %>% 
  setorder(-Propensity) ->
  ate_data
```


# Average Treatment Effects - Quality Life

```{r ate_ql, warning=FALSE, echo=FALSE, comment="", include=FALSE}
outcomes <- matching_vars$outcomes_ql

# predictive_variates <- c(matching_vars$covariates, matching_vars$predictive) %>% unique

predictive_variates <- c(treatment_name, 'Propensity')
results_outcomes <- list()
for(outcome in outcomes){
  is_classification <- class(ate_data[[outcome]]) %in% c('character', 'factor')
  results_outcomes[[outcome]] <- calc_ate(
    ate_data, outcome, treatment_name=treatment_name, predictive_variates, first_visit=TRUE, tuneLenghtATE, modelsATE, incremental=TRUE, is_classification
  )
}
```

```{r echo=FALSE, warning=FALSE, comment=""}
for(outcome in outcomes){
  is_classification <- class(sel_data[[outcome]]) %in% c('character', 'factor')
  print_ates(treatment_name, outcome, results_outcomes[[outcome]], is_classification)
}
```

# Average Treatment Effects - Radiology

```{r ate_radio, warning=FALSE, echo=FALSE, comment="", include=FALSE}
outcomes <- matching_vars$outcomes_radiology

# predictive_variates <- c(matching_vars$covariates, matching_vars$predictive) %>% unique
predictive_variates <- c(treatment_name, 'Propensity')
results_outcomes <- list()
for(outcome in outcomes){
  is_classification <- class(ate_data[[outcome]]) %in% c('character', 'factor')
  results_outcomes[[outcome]] <- calc_ate(
    ate_data, outcome, treatment_name=treatment_name, predictive_variates, first_visit=FALSE,
    tuneLenghtATE, modelsATE, incremental=TRUE, is_classification
  )
}
```

```{r echo=FALSE, warning=FALSE, comment=""}
for(outcome in outcomes){
  is_classification <- class(sel_data[[outcome]]) %in% c('character', 'factor')
  print_ates(treatment_name, outcome, results_outcomes[[outcome]], is_classification)
}
```

# Average Treatment Effects - Complications

```{r ate_complication, warning=FALSE, echo=FALSE, comment="", include=FALSE}
xls_path <- 'data/ESSG extraction July 2020_3.xlsx'
# excel_sheets(xls_path)

patients_complications <- read_excel(xls_path, sheet='Complications') %>%
  as.data.table %>%
  .[`Complication Type`=='Primary'] %>%
  .[`Reoperation Due to Complication`=='Yes'] %>%
  .[, `Code of the patient`]

data_ <- ate_data %>%
  copy %>%
  .[, complication:='No'] %>%
  .[`Code of the patient` %in% patients_complications, complication:='Yes']

outcome <- 'complication'
is_classification <- TRUE
predictive_variates <- c(
  matching_vars$covariates, matching_vars$predictive, 'Propensity'
) %>% unique
results <- calc_ate(
    data_, outcome, treatment_name=treatment_name, predictive_variates, first_visit=FALSE,
    tuneLenghtATE, modelsATE, incremental=FALSE, is_classification
)
```

```{r echo=FALSE, warning=FALSE, comment=""}
print_ates(treatment_name, outcome, results, is_classification)
```

# Average Treatment Effects - Nombre Revisions

```{r ate_reintervention, warning=FALSE, echo=FALSE, comment="", include=FALSE}
xls_path <- 'data/ESSG extraction July 2020_3.xlsx'
# excel_sheets(xls_path)

rev_patient_data <- read_excel(xls_path, sheet = "Rev surgeries") %>% 
  data.table %>% 
  .[, .(reinterventions=.N), `Code of the patient`]

data_ <- ate_data %>%
  copy %>%
  merge(rev_patient_data, by="Code of the patient", all.x=TRUE, all.y=FALSE) %>% 
  .[is.na(reinterventions), reinterventions:=0] %>% 
  .[, `Code of the patient`:=NULL]

outcome <- 'reinterventions'
is_classification <- FALSE
predictive_variates <- c(
  matching_vars$covariates, matching_vars$predictive, 'Propensity'
) %>% unique
results <- calc_ate(
    data_, outcome, treatment_name=treatment_name, predictive_variates, first_visit=FALSE,
    tuneLenghtATE, modelsATE, incremental=FALSE, is_classification
)
```

```{r echo=FALSE, warning=FALSE, comment=""}
print_ates(treatment_name, outcome, results, is_classification)
```